
---
title: "Model Validation and Simulation Data"
output: html_document
author: "Hayato Yoshioka (University of Tokyo, AgroParisTech)"
---

# Overview. H.Yoshioka et al. (rrda package)

Simluation to obtain Lambda max computation for rrda

The rrda function computes the range of lambda based on the method odf glmnet. To obtain the range, it coputes the crossproduct of X and Y. However, for a large matrix (X,Y), it is better to avoid the cross product because it requires large memories and takes time.

Here, we propose the sampling method for X and Y, (1000 sampling) for a matrix which has many variables for X and Y (p>1000 or q>1000).

To validate the model, we define four functions:

1. **gl2**: No sampling is performed  
2. **gl3**: Both X and Y are sampled  
3. **gl3x**: Only X is sampled  
4. **gl3y**: Only Y is sampled  

We generate simulation data based on two parameter rules:

1. **Rule 1**:  
   - \(n = 10 - 100\)  
   - \(p = 100,000\)  
   - \(q = 10,000\)

2. **Rule 2**:  
   - \(n = 10 - 100\)  
   - \(p = 1,000,000\)  
   - \(q = 100\)



# package 
```{r}
library(tictoc)
library(here)
```

# functions
```{r}

gl2 <- function(Y, X) {
  usx<-unb(X)
  usy<-unb(Y)
  tmp_sum<- colSums(crossprod(usy,usx)^2)
  result <- max(sqrt(tmp_sum)) / (nrow(Y) * 10^(-3))
  e<- 10^seq(-4,0, length.out = 50)
  lambda_def<- result * e
  lambda_def<- signif(lambda_def,4)
  return(lambda_def)
}


gl3 <- function(Y, X) {
  y_rate<- 1
  if(ncol(X)>1000){
   X<-X[,sample(ncol(X), 1000, replace = FALSE)]
  }
  if(ncol(Y)>1000){
   y_rate<- ncol(Y)/1000
   Y<-Y[,sample(ncol(Y), 1000, replace = FALSE)]
  }
  usx<-unb(X)
  usy<-unb(Y)
  
  tmp_sum<- colSums((crossprod(usy,usx))^2) * y_rate
  result <- max(sqrt(tmp_sum)) / (nrow(Y) * 10^(-3))
  e<- 10^seq(-4,0, length.out = 50)
  lambda_def<- result * e
  lambda_def<- signif(lambda_def,4)
  return(lambda_def)
}


gl3x <- function(Y, X) {
 #y_rate<- 1
  if(ncol(X)>1000){
   X<-X[,sample(ncol(X), 1000, replace = FALSE)]
  }
 
  usx<-unb(X)
  usy<-unb(Y)
  
  
  tmp_sum<- colSums((crossprod(usy,usx))^2) #* y_rate
  result <- max(sqrt(tmp_sum)) / (nrow(Y) * 10^(-3))
  e<- 10^seq(-4,0, length.out = 50)
  lambda_def<- result * e
  lambda_def<- signif(lambda_def,4)
  return(lambda_def)
}


gl3y <- function(Y, X) {
  y_rate<- 1
  
  if(ncol(Y)>1000){
   y_rate<- ncol(Y)/1000
   Y<-Y[,sample(ncol(Y), 1000, replace = FALSE)]
  }
  usx<-unb(X)
  usy<-unb(Y)

  
  tmp_sum<- colSums((crossprod(usy,usx))^2) * y_rate
  result <- max(sqrt(tmp_sum)) / (nrow(Y) * 10^(-3))
  e<- 10^seq(-4,0, length.out = 50)
  lambda_def<- result * e
  lambda_def<- signif(lambda_def,4)
  return(lambda_def)
}

# unbiased scaling function, used for other functions, 
unb <- function(x) {

  l <- nrow(x)
  xx<-scale(x) / sqrt((l-1)/l)
  xx[is.na(xx)] <- 0
  return(xx)
}

```

# Matrix rule 1

## Run

Simulation is performed to valudate the subsampling method for obtaining lambda range
```{r,eval=F}
#set.seed(123)
set.seed(123)
num<-100
Res_gl3y_vec <- numeric(num)
Res_gl3x_vec <- numeric(num)
Res_gl3_vec <- numeric(num)
Res_gl2_vec <- numeric(num)
Time_gl3y_vec <- numeric(num)
Time_gl3x_vec <- numeric(num)
Time_gl3_vec <- numeric(num)
Time_gl2_vec <- numeric(num)

n_list <- sample(10:100, num, replace = TRUE)
p <- 100000
q <- 10000

pb <- txtProgressBar(min = 0, max = num, style = 3)
for (i in 1:num) {

  n <- n_list[i]

  X <- matrix(rnorm(n * p), n, p)
  Y <- matrix(rnorm(n * q), n, q)
 
  time_gl3 <- system.time({
    Res_gl3 <- gl3(Y, X)[50] 
  })[3]
  
  time_gl3x <- system.time({
    Res_gl3x <- gl3x(Y, X)[50] 
  })[3]
  
  time_gl3y <- system.time({
    Res_gl3y <- gl3y(Y, X)[50] 
  })[3]  

  time_gl2 <- system.time({
    Res_gl2 <- gl2(Y, X)[50]  
  })[3]

  Res_gl3x_vec[i] <- Res_gl3x
  Res_gl3y_vec[i] <- Res_gl3y
  Res_gl3_vec[i] <- Res_gl3
  Res_gl2_vec[i] <- Res_gl2
  Time_gl3x_vec[i] <- time_gl3x
  Time_gl3y_vec[i] <- time_gl3y
  Time_gl3_vec[i] <- time_gl3
  Time_gl2_vec[i] <- time_gl2

  setTxtProgressBar(pb, i)
  
  }
close(pb)

results <- list(
  Res_gl3 = Res_gl3_vec,
  Res_gl3x = Res_gl3x_vec,
  Res_gl3y = Res_gl3y_vec,
  Res_gl2 = Res_gl2_vec,
  Time_gl3 = Time_gl3_vec,
  Time_gl3x = Time_gl3x_vec,
  Time_gl3y = Time_gl3y_vec,
  Time_gl2 = Time_gl2_vec,
  n_list = n_list,
  # p_list = p_list,
  # q_list = q_list
  p_list = p,
  q_list = q
)

#print(results)

saveRDS(results,here("out","lambda_sim_large.RDS"))

```

## Results
Plot the results
```{r,warning=FALSE}
results<-readRDS(here("out","lambda_sim_large.RDS"))

Res_gl2_vec <- results$Res_gl2
Res_gl3_vec <- results$Res_gl3
Res_gl3x_vec <-results$Res_gl3x
Res_gl3y_vec <-results$Res_gl3y


Time_gl2_vec <- results$Time_gl2
Time_gl3_vec <- results$Time_gl3
Time_gl3x_vec <-results$Time_gl3x
Time_gl3y_vec <-results$Time_gl3y

plot(Res_gl2_vec,Res_gl3_vec,main="Max Lambda (Sampling both X and Y)", xlab="FULL", ylab="Sampled",ylim = c(0,max(Res_gl2_vec)))
abline(0,1,col=2)

plot(Res_gl2_vec,Res_gl3x_vec,main="Max Lambda (Sampling only X)", xlab="FULL", ylab="Sampled",ylim = c(0,max(Res_gl2_vec)))
abline(0,1,col=2)

plot(Res_gl2_vec,Res_gl3y_vec,main="Max Lambda (Sampling only Y)", xlab="FULL", ylab="Sampled",ylim = c(0,max(Res_gl2_vec)))
abline(0,1,col=2)

plot(Time_gl2_vec,Time_gl3_vec,main="Computation time",ylim = c(0,max(Time_gl2_vec)))
abline(0,1,col=2)

plot(Time_gl2_vec,Time_gl3x_vec,main="Computation time",ylim = c(0,max(Time_gl2_vec)))
abline(0,1,col=2)

plot(Time_gl3_vec,Time_gl3y_vec,main="Computation time",ylim = c(0,max(Time_gl2_vec)))
abline(0,1,col=2)

mean(Time_gl2_vec)
mean(Time_gl3_vec)
mean(Time_gl3x_vec)
mean(Time_gl3y_vec)



# Calculating the mean of each vector
means <- c(mean(Time_gl2_vec), mean(Time_gl3_vec), mean(Time_gl3x_vec), mean(Time_gl3y_vec))

# Calculating the standard error for each vector
stderr <- function(x) sd(x) / sqrt(length(x))
errors <- c(stderr(Time_gl2_vec), stderr(Time_gl3_vec), stderr(Time_gl3x_vec), stderr(Time_gl3y_vec))

# Defining labels for the vectors
labels <- c("Full", "XY_sampling", "X_sampling", "Y_sampling")

# Setting colors for the bars
colors <- c("#3498db", "#2ecc71", "#e74c3c", "#9b59b6")

# Creating the barplot
bp <- barplot(means, names.arg = labels, col = colors, ylim = c(0, max(means + errors) + 5),
              main = "Computation time", ylab = "Mean Values")

# Adding error bars
arrows(bp, means - errors, bp, means + errors, angle = 90, code = 3, length = 0.1, col = "black")
# Adding mean values above each bar
text(bp, means + errors + 1.2, labels = round(means, 2), cex = 1, col = "black")


df <- data.frame(
  Full = Res_gl2_vec,
  XY_sampling= Res_gl3_vec,
  X_sampling = Res_gl3x_vec,
  Y_Sampling = Res_gl3y_vec
)

panel.plot <- function(x, y) {
  points(x, y, pch = 1)
 abline(0, 1, col = "red") 
}


panel.cor <- function(x, y) {

  par(usr = c(0, 1, 0, 1))
  r <- round(cor(x, y), digits=6)
  txt <- paste0("r = ", r)
  text(0.5, 0.5, txt, cex = 1.6)
}


pairs(df, 
      lower.panel = panel.plot,  
      upper.panel = panel.cor,
      diag.panel = NULL)         
```

# Matrix rule 2

## Run 
Simulation is performed to valudate the subsampling method for obtaining lambda range
```{r,eval=F}
set.seed(123)
num<-100
Res_gl3y_vec <- numeric(num)
Res_gl3x_vec <- numeric(num)
Res_gl3_vec <- numeric(num)
Res_gl2_vec <- numeric(num)
Time_gl3y_vec <- numeric(num)
Time_gl3x_vec <- numeric(num)
Time_gl3_vec <- numeric(num)
Time_gl2_vec <- numeric(num)

n_list <- sample(10:100, num, replace = TRUE)
p <- 1000000
q <- 100

pb <- txtProgressBar(min = 0, max = num, style = 3)
for (i in 1:num) {

  n <- n_list[i]

  X <- matrix(rnorm(n * p), n, p)
  Y <- matrix(rnorm(n * q), n, q)
 
  time_gl3 <- system.time({
    Res_gl3 <- gl3(Y, X)[50] 
  })[3]
  
  time_gl3x <- system.time({
    Res_gl3x <- gl3x(Y, X)[50] 
  })[3]
  
  time_gl3y <- system.time({
    Res_gl3y <- gl3y(Y, X)[50] 
  })[3]  

  time_gl2 <- system.time({
    Res_gl2 <- gl2(Y, X)[50]  
  })[3]

  Res_gl3x_vec[i] <- Res_gl3x
  Res_gl3y_vec[i] <- Res_gl3y
  Res_gl3_vec[i] <- Res_gl3
  Res_gl2_vec[i] <- Res_gl2
  Time_gl3x_vec[i] <- time_gl3x
  Time_gl3y_vec[i] <- time_gl3y
  Time_gl3_vec[i] <- time_gl3
  Time_gl2_vec[i] <- time_gl2

  setTxtProgressBar(pb, i)
  
  }
close(pb)

results <- list(
  Res_gl3 = Res_gl3_vec,
  Res_gl3x = Res_gl3x_vec,
  Res_gl3y = Res_gl3y_vec,
  Res_gl2 = Res_gl2_vec,
  Time_gl3 = Time_gl3_vec,
  Time_gl3x = Time_gl3x_vec,
  Time_gl3y = Time_gl3y_vec,
  Time_gl2 = Time_gl2_vec,
  n_list = n_list,
  # p_list = p_list,
  # q_list = q_list
  p_list = p,
  q_list = q
)


saveRDS(results,here("out","lambda_sim_large2.RDS"))

```

## Results
Plot results
```{r,warning=FALSE}

results<-readRDS(here("out","lambda_sim_large2.RDS"))

Res_gl2_vec <- results$Res_gl2
Res_gl3_vec <- results$Res_gl3
Res_gl3x_vec <-results$Res_gl3x
Res_gl3y_vec <-results$Res_gl3y


Time_gl2_vec <- results$Time_gl2
Time_gl3_vec <- results$Time_gl3
Time_gl3x_vec <-results$Time_gl3x
Time_gl3y_vec <-results$Time_gl3y

plot(Res_gl2_vec,Res_gl3_vec,main="Max Lambda (Sampling both X and Y)", xlab="FULL", ylab="Sampled",ylim = c(0,max(Res_gl2_vec)))
abline(0,1,col=2)

plot(Res_gl2_vec,Res_gl3x_vec,main="Max Lambda (Sampling only X)", xlab="FULL", ylab="Sampled",ylim = c(0,max(Res_gl2_vec)))
abline(0,1,col=2)

plot(Res_gl2_vec,Res_gl3y_vec,main="Max Lambda (Sampling only Y)", xlab="FULL", ylab="Sampled",ylim = c(0,max(Res_gl2_vec)))
abline(0,1,col=2)

plot(Time_gl2_vec,Time_gl3_vec,main="Computation time",ylim = c(0,max(Time_gl2_vec)))
abline(0,1,col=2)

plot(Time_gl2_vec,Time_gl3x_vec,main="Computation time",ylim = c(0,max(Time_gl2_vec)))
abline(0,1,col=2)

plot(Time_gl3_vec,Time_gl3y_vec,main="Computation time",ylim = c(0,max(Time_gl2_vec)))
abline(0,1,col=2)

mean(Time_gl2_vec)
mean(Time_gl3_vec)
mean(Time_gl3x_vec)
mean(Time_gl3y_vec)

# Calculating the mean of each vector
means <- c(mean(Time_gl2_vec), mean(Time_gl3_vec), mean(Time_gl3x_vec), mean(Time_gl3y_vec))

# Calculating the standard error for each vector
stderr <- function(x) sd(x) / sqrt(length(x))
errors <- c(stderr(Time_gl2_vec), stderr(Time_gl3_vec), stderr(Time_gl3x_vec), stderr(Time_gl3y_vec))

# Defining labels for the vectors
labels <- c("Full", "XY_sampling", "X_sampling", "Y_sampling")

# Setting colors for the bars
colors <- c("#3498db", "#2ecc71", "#e74c3c", "#9b59b6")

# Creating the barplot
bp <- barplot(means, names.arg = labels, col = colors, ylim = c(0, max(means + errors) + 2),
              main = "Comparison of Vector Means with Error Bars", ylab = "Mean Values")

# Adding error bars
arrows(bp, means - errors, bp, means + errors, angle = 90, code = 3, length = 0.1, col = "black")
text(bp, means + errors + 0.5, labels = round(means, 2), cex = 1, col = "black")


df <- data.frame(
  Full = Res_gl2_vec,
  XY_sampling= Res_gl3_vec,
  X_sampling = Res_gl3x_vec,
  Y_Sampling = Res_gl3y_vec
)

panel.plot <- function(x, y) {
  points(x, y, pch = 1)
 abline(0, 1, col = "red") 
}


panel.cor <- function(x, y) {

  par(usr = c(0, 1, 0, 1))
  r <- round(cor(x, y), digits=6)
  txt <- paste0("r = ", r)
  text(0.5, 0.5, txt, cex = 1.6)
}


pairs(df, 
      lower.panel = panel.plot,   
      upper.panel = panel.cor,     
			
			
      diag.panel = NULL)         


```

# session info
check the info and environment
```{r}
devtools::session_info()
```
