---
title: "Senario 2 : Rank Estimate Evaluation on Simulation Data with RRDA"
output: html_document
author: "Hayato Yoshioka (University of Tokyo, AgroParisTech)"
---

# Overview. H.Yoshioka et al. (rrda package)

Senario 2

Here, we perform rank evaluation for simulation data sets.
We test various n,p,q,k parameters for the data generation

We evaluate the model by checking the percentage of the right rank estimation and the correlation between true and estimated rank.

Test all combinations of
n = c(100,200),
pq = c(50, 100, 200,500),
k = c(2, 5, 10)

For each, 20 iterations.

# package
```{r}
library(furrr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(RSpectra)
library(rrda)
library(xtable)
library(purrr) 
library(here)
library(progress)
source("script_rrda/functions_rrda_yoshioka.R")
source("script_rrda/functions_stars_rrr_yoshioka.R")
library(furrr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(RSpectra)
library(rrda)
library(here)
library(xtable)
library(pheatmap)
library(tictoc)
library(tidyr)
library(tibble)
library(here)
library(xtable)
library(rrpack)

```

# s2n 1 (mid noise)
Create the folder for saving
```{r}
dir_path<- here("out/eval_1")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
}

```

```{r}
rdasim1<- function(n,p,q,k,s2n = c(1, 1)){
  H  <- matrix(stats::rnorm(n = n*k, mean = 0, sd = 1),n,k)
  
  theta.x  <- matrix(stats::rnorm(n = k*p, mean = 0, sd = 1),k,p)
  noise.x <-  matrix(stats::rnorm(n = n*p, mean = 0, sd = 1),n,p)
  
  signal.x <- H %*% theta.x
  sigma.x <- sqrt(sum(signal.x^2) / (sum(noise.x^2) * s2n[1]))
  noise.x <- sigma.x * noise.x

  X  <- signal.x + noise.x
  
  theta.y  <- matrix(stats::rnorm(n = k*q, mean = 0, sd = 1),k,q)
  noise.y  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  
  signal.y <- H %*% theta.y
  sigma.y <- sqrt(sum(signal.y^2) / (sum(noise.y^2) * s2n[2]))
  noise.y <- sigma.y * noise.y


  Y  <- signal.y + noise.y

  return(list(X=X,Y=Y,H=H,theta.y=theta.y))
}

rdasim2<- function(n,p,q,k,s2n=1,xofd=0){
  cov <- matrix(xofd, nrow = p, ncol = p)
  diag(cov) <- 1
  X  <- MASS::mvrnorm(n, rep(0, p), cov)

  A <- matrix(stats::rnorm(n = p * k, mean = 0, sd = 1), p, k)
  A <- apply(A, 2, function(col) col / sqrt(sum(col^2)))
  C <- matrix(stats::rnorm(n = k * q, mean = 0, sd = 1), k, q)
  C <- apply(C, 2, function(col) col / sqrt(sum(col^2)))

  B  <- crossprod(t(A),C)
  E  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  XB <- crossprod(t(X),B)
  sigma <- sqrt(sum(XB^2) / (sum(E^2) * s2n))
  E  <- E * sigma
  Y <- XB + E
  return(list(X=X,Y=Y,B=B,E=E))
}


```

# simulation run 
2 types of simulations and 2 size of n, 3 size of p and q, 3 size of r

```{r,eval=F}
set.seed(123)

n_iterations=20
# Define your conditions
simulations <- c("sim1","sim2")
sizes <- c( "small","large")

#simulations <- c("sim2")
#sizes <- c("large")

# Loop over each combination
for (sim in simulations) {

  for (size in sizes) {
    # Run your function with each combination
    data_list <- rank_evaluate_50_allcriteria_200(n_iterations = n_iterations, rdasim = sim, size = size)
    # Save the results
    filename <- paste0("data_list50_", sim, "_", size, "_all200.rds")
    saveRDS(data_list, file = here(dir_path, filename))
    data_list<-readRDS(here(dir_path, filename))
    pp<-plot_evaluate_all(data_list,rdasim = sim,size=size,n_iterations)
    pp
  }
}

```

# get result

```{r}
simulations <- c("sim1","sim2")
sizes <- c("large", "small")
n_iterations<-20
#sizes <- c("large")
 
for (sim in simulations) {
  cat("Simulation:", sim, "\n")
  
  emat_list <- list()  # List to store emat for each size
  
  for (size in sizes) {
    #cat("Size:", size, "\n")
    
    filename <- paste0("data_list50_", sim, "_", size, "_all200.rds")
    data_list <- readRDS(here(dir_path, filename))
    
    # Compute accuracy matrix
    emat <- plot_evaluate_by_true_rank4(data_list, rdasim = sim, size = size, n_iterations)
    
    # Store as matrix
    emat_list[[as.character(size)]] <- as.matrix(emat)

  }
combined_emat <- list()

for (k_name in rownames(emat_list$large)) {
  combined_emat[[k_name]] <- list()
  
  method_names <- names(emat_list$large[k_name, ][[1]])
  
  for (method in method_names) {
    vec_large <- emat_list$large[k_name, ][[1]][[method]]
    vec_small <- emat_list$small[k_name, ][[1]][[method]]
    combined_vec <- c(vec_small, vec_large)

    combined_emat[[k_name]][[method]] <- combined_vec
  }
}

# Prepare summary data frame
summary_df <- data.frame()

for (k_name in names(combined_emat)) {
  for (method in names(combined_emat[[k_name]])) {
    values <- combined_emat[[k_name]][[method]]
    n <- length(values)
    mean_val <- round(mean(values, na.rm = TRUE),2)
    se_val <- round(sd(values, na.rm = TRUE) / sqrt(n),2)

    summary_df <- rbind(summary_df, data.frame(
      Method = method,
      k = k_name,
      Mean = mean_val,
      SE = se_val
    ))
  }
}

# Convert to wide format
mean_table <- summary_df %>%
  select(Method, k, Mean) %>%
  pivot_wider(names_from = k, values_from = Mean)

se_table <- summary_df %>%
  select(Method, k, SE) %>%
  pivot_wider(names_from = k, values_from = SE)

# Add Overall column
mean_table$Overall <- round(rowMeans(mean_table[,-1], na.rm = TRUE),2)
se_table$Overall <- round(rowMeans(se_table[,-1], na.rm = TRUE),2)

# Display results
print(mean_table[,c(1:4)])
print(se_table[,c(1:4)])
}


```



```{r}

for (sim in simulations) {
  #cat("Simulation:", sim, "\n")
  
  emat_list <- list()  # List to store emat for each size
  
  for (size in sizes) {
    #cat("Size:", size, "\n")
    
    filename <- paste0("data_list50_", sim, "_", size, "_all200.rds")
    data_list <- readRDS(here(dir_path, filename))
    
    # Compute accuracy matrix
    emat <- plot_evaluate_by_true_rank4(data_list, rdasim = sim, size = size, n_iterations)
    
    # Store as matrix
    emat_list[[as.character(size)]] <- as.matrix(emat)

  }
combined_emat <- list()

for (k_name in rownames(emat_list$large)) {
  combined_emat[[k_name]] <- list()
  
  method_names <- names(emat_list$large[k_name, ][[1]])
  
  for (method in method_names) {
    vec_large <- emat_list$large[k_name, ][[1]][[method]]
    vec_small <- emat_list$small[k_name, ][[1]][[method]]
    combined_vec <- c(vec_small, vec_large)

    combined_emat[[k_name]][[method]] <- combined_vec
  }
}


combo <- expand.grid(
  n = c(100,200),
  pq = c(50, 100, 200,500),
  k = c(2, 5, 10)
)

results_df <- combo
method_names <- names(combined_emat[[1]])

for (k_name in names(combined_emat)) {
  k_val <- as.numeric(sub("k=", "", k_name))
  combo_idx <- which(combo$k == k_val)
  n_combo_k <- length(combo_idx)

  for (method in method_names) {
    values <- combined_emat[[k_name]][[method]]

    mat <- matrix(values, nrow = n_iterations, ncol =n_combo_k , byrow = FALSE)

    # 平均と SE を計算
    mean_vals <- colMeans(mat)
    se_vals <- round(apply(mat, 2, sd) / sqrt(n_iterations),2)

    # 列名を設定
    mean_colname <- paste0(method, "_mean")
    se_colname <- paste0(method, "_se")

    # 必要なら列を初期化
    if (!mean_colname %in% colnames(results_df)) {
      results_df[[mean_colname]] <- NA
    }
    if (!se_colname %in% colnames(results_df)) {
      results_df[[se_colname]] <- NA
    }

    # 結果を代入
    results_df[combo_idx, mean_colname] <- mean_vals
    results_df[combo_idx, se_colname] <- se_vals
  }
}

print(results_df)

saveRDS(results_df,file = here(dir_path, paste0(sim,"rdf200.rds")))

}

```



# s2n 10 (low noise)
Create the folder for saving
```{r}
dir_path<- here("out/eval_10")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
}

```



```{r}
rdasim1<- function(n,p,q,k,s2n = c(10, 10)){
  H  <- matrix(stats::rnorm(n = n*k, mean = 0, sd = 1),n,k)
  
  theta.x  <- matrix(stats::rnorm(n = k*p, mean = 0, sd = 1),k,p)
  noise.x <-  matrix(stats::rnorm(n = n*p, mean = 0, sd = 1),n,p)
  
  signal.x <- H %*% theta.x
  sigma.x <- sqrt(sum(signal.x^2) / (sum(noise.x^2) * s2n[1]))
  noise.x <- sigma.x * noise.x

  X  <- signal.x + noise.x
  
  theta.y  <- matrix(stats::rnorm(n = k*q, mean = 0, sd = 1),k,q)
  noise.y  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  
  signal.y <- H %*% theta.y
  sigma.y <- sqrt(sum(signal.y^2) / (sum(noise.y^2) * s2n[2]))
  noise.y <- sigma.y * noise.y


  Y  <- signal.y + noise.y

  return(list(X=X,Y=Y,H=H,theta.y=theta.y))
}

rdasim2<- function(n,p,q,k,s2n=10,xofd=0){
  cov <- matrix(xofd, nrow = p, ncol = p)
  diag(cov) <- 1
  X  <- MASS::mvrnorm(n, rep(0, p), cov)

  A <- matrix(stats::rnorm(n = p * k, mean = 0, sd = 1), p, k)
  A <- apply(A, 2, function(col) col / sqrt(sum(col^2)))
  C <- matrix(stats::rnorm(n = k * q, mean = 0, sd = 1), k, q)
  C <- apply(C, 2, function(col) col / sqrt(sum(col^2)))

  B  <- crossprod(t(A),C)
  E  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  XB <- crossprod(t(X),B)
  sigma <- sqrt(sum(XB^2) / (sum(E^2) * s2n))
  E  <- E * sigma
  Y <- XB + E
  return(list(X=X,Y=Y,B=B,E=E))
}


```


# simulation run 
2 types of simulations and 2 size of n, 3 size of p and q, 3 size of r

```{r,eval=F}
set.seed(123)

n_iterations=20
# Define your conditions
simulations <- c("sim1","sim2")
sizes <- c("large", "small")

#simulations <- c("sim1")
#sizes <- c("small")

# Loop over each combination
for (sim in simulations) {

  for (size in sizes) {
    # Run your function with each combination
    data_list <- rank_evaluate_50_allcriteria_200(n_iterations = n_iterations, rdasim = sim, size = size)
    # Save the results
    filename <- paste0("data_list50_", sim, "_", size, "_all200.rds")
    saveRDS(data_list, file = here(dir_path, filename))
    data_list<-readRDS(here(dir_path, filename))
    pp<-plot_evaluate_all(data_list,rdasim = sim,size=size,n_iterations)
    pp
  }
}

```

# get result
```{r}
simulations <- c("sim1","sim2")
#sizes <- c("large")
 
for (sim in simulations) {
  cat("Simulation:", sim, "\n")
  
  emat_list <- list()  # List to store emat for each size
  
  for (size in sizes) {
    cat("Size:", size, "\n")
    
    filename <- paste0("data_list50_", sim, "_", size, "_all200.rds")
    data_list <- readRDS(here(dir_path, filename))
    
    # Compute accuracy matrix
    emat <- plot_evaluate_by_true_rank4(data_list, rdasim = sim, size = size, n_iterations)
    
    # Store as matrix
    emat_list[[as.character(size)]] <- as.matrix(emat)

  }
combined_emat <- list()

for (k_name in rownames(emat_list$large)) {
  combined_emat[[k_name]] <- list()
  
  method_names <- names(emat_list$large[k_name, ][[1]])
  
  for (method in method_names) {
    vec_large <- emat_list$large[k_name, ][[1]][[method]]
    vec_small <- emat_list$small[k_name, ][[1]][[method]]
    combined_vec <- c(vec_small, vec_large)

    combined_emat[[k_name]][[method]] <- combined_vec
  }
}

# Prepare summary data frame
summary_df <- data.frame()

for (k_name in names(combined_emat)) {
  for (method in names(combined_emat[[k_name]])) {
    values <- combined_emat[[k_name]][[method]]
    n <- length(values)
    mean_val <- round(mean(values, na.rm = TRUE),2)
    se_val <- round(sd(values, na.rm = TRUE) / sqrt(n),2)

    summary_df <- rbind(summary_df, data.frame(
      Method = method,
      k = k_name,
      Mean = mean_val,
      SE = se_val
    ))
  }
}

# Convert to wide format
mean_table <- summary_df %>%
  select(Method, k, Mean) %>%
  pivot_wider(names_from = k, values_from = Mean)

se_table <- summary_df %>%
  select(Method, k, SE) %>%
  pivot_wider(names_from = k, values_from = SE)

# Add Overall column
mean_table$Overall <- round(rowMeans(mean_table[,-1], na.rm = TRUE),2)
se_table$Overall <- round(rowMeans(se_table[,-1], na.rm = TRUE),2)

# Display results
print(mean_table[,c(1:4)])
print(se_table[,c(1:4)])
}


```



```{r}

for (sim in simulations) {
  #cat("Simulation:", sim, "\n")
  
  emat_list <- list()  # List to store emat for each size
  
  for (size in sizes) {
    #cat("Size:", size, "\n")
    
    filename <- paste0("data_list50_", sim, "_", size, "_all200.rds")
    data_list <- readRDS(here(dir_path, filename))
    
    # Compute accuracy matrix
    emat <- plot_evaluate_by_true_rank4(data_list, rdasim = sim, size = size, n_iterations)
    
    # Store as matrix
    emat_list[[as.character(size)]] <- as.matrix(emat)

  }
combined_emat <- list()

for (k_name in rownames(emat_list$large)) {
  combined_emat[[k_name]] <- list()
  
  method_names <- names(emat_list$large[k_name, ][[1]])
  
  for (method in method_names) {
    vec_large <- emat_list$large[k_name, ][[1]][[method]]
    vec_small <- emat_list$small[k_name, ][[1]][[method]]
    combined_vec <- c(vec_small, vec_large)

    combined_emat[[k_name]][[method]] <- combined_vec
  }
}


combo <- expand.grid(
  n = c(100,200),
  pq = c(50, 100, 200,500),
  k = c(2, 5, 10)
)

results_df <- combo
method_names <- names(combined_emat[[1]])

for (k_name in names(combined_emat)) {
  k_val <- as.numeric(sub("k=", "", k_name))
  combo_idx <- which(combo$k == k_val)
  n_combo_k <- length(combo_idx)

  for (method in method_names) {
    values <- combined_emat[[k_name]][[method]]

    mat <- matrix(values, nrow = n_iterations, ncol =n_combo_k , byrow = FALSE)

    # 平均と SE を計算
    mean_vals <- colMeans(mat)
    se_vals <- round(apply(mat, 2, sd) / sqrt(n_iterations),2)

    # 列名を設定
    mean_colname <- paste0(method, "_mean")
    se_colname <- paste0(method, "_se")

    # 必要なら列を初期化
    if (!mean_colname %in% colnames(results_df)) {
      results_df[[mean_colname]] <- NA
    }
    if (!se_colname %in% colnames(results_df)) {
      results_df[[se_colname]] <- NA
    }

    # 結果を代入
    results_df[combo_idx, mean_colname] <- mean_vals
    results_df[combo_idx, se_colname] <- se_vals
  }
}

print(results_df)

saveRDS(results_df,file = here(dir_path, paste0(sim,"rdf200.rds")))

}

```

# s2n 0.1 (high noise)

Create the folder for saving
```{r}
dir_path<- here("out/eval_01")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
}

```


```{r}
rdasim1<- function(n,p,q,k,s2n = c(0.1, 0.1)){
  H  <- matrix(stats::rnorm(n = n*k, mean = 0, sd = 1),n,k)
  
  theta.x  <- matrix(stats::rnorm(n = k*p, mean = 0, sd = 1),k,p)
  noise.x <-  matrix(stats::rnorm(n = n*p, mean = 0, sd = 1),n,p)
  
  signal.x <- H %*% theta.x
  sigma.x <- sqrt(sum(signal.x^2) / (sum(noise.x^2) * s2n[1]))
  noise.x <- sigma.x * noise.x

  X  <- signal.x + noise.x
  
  theta.y  <- matrix(stats::rnorm(n = k*q, mean = 0, sd = 1),k,q)
  noise.y  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  
  signal.y <- H %*% theta.y
  sigma.y <- sqrt(sum(signal.y^2) / (sum(noise.y^2) * s2n[2]))
  noise.y <- sigma.y * noise.y


  Y  <- signal.y + noise.y

  return(list(X=X,Y=Y,H=H,theta.y=theta.y))
}

rdasim2<- function(n,p,q,k,s2n=0.1,xofd=0){
  cov <- matrix(xofd, nrow = p, ncol = p)
  diag(cov) <- 1
  X  <- MASS::mvrnorm(n, rep(0, p), cov)

  A <- matrix(stats::rnorm(n = p * k, mean = 0, sd = 1), p, k)
  A <- apply(A, 2, function(col) col / sqrt(sum(col^2)))
  C <- matrix(stats::rnorm(n = k * q, mean = 0, sd = 1), k, q)
  C <- apply(C, 2, function(col) col / sqrt(sum(col^2)))

  B  <- crossprod(t(A),C)
  E  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  XB <- crossprod(t(X),B)
  sigma <- sqrt(sum(XB^2) / (sum(E^2) * s2n))
  E  <- E * sigma
  Y <- XB + E
  return(list(X=X,Y=Y,B=B,E=E))
}


```

# simulation run 
2 types of simulations and 2 size of n, 3 size of p and q, 3 size of r

```{r,eval=F}
set.seed(123)

n_iterations=20
# Define your conditions
simulations <- c("sim1","sim2")
sizes <- c("large", "small")

#simulations <- c("sim1")
#sizes <- c("small")

# Loop over each combination
for (sim in simulations) {

  for (size in sizes) {
    # Run your function with each combination
    data_list <- rank_evaluate_50_allcriteria_200(n_iterations = n_iterations, rdasim = sim, size = size)
    # Save the results
    filename <- paste0("data_list50_", sim, "_", size, "_all200.rds")
    saveRDS(data_list, file = here(dir_path, filename))
    data_list<-readRDS(here(dir_path, filename))
    pp<-plot_evaluate_all(data_list,rdasim = sim,size=size,n_iterations)
    pp
  }
}

```

# get result
Plot the results

```{r}

n_iterations=20
#sizes <- c("large")
simulations <- c("sim1","sim2")
for (sim in simulations) {
  cat("Simulation:", sim, "\n")
  
  emat_list <- list()  # List to store emat for each size
  
  for (size in sizes) {
    cat("Size:", size, "\n")
    
    filename <- paste0("data_list50_", sim, "_", size, "_all200.rds")
    data_list <- readRDS(here(dir_path, filename))
    
    # Compute accuracy matrix
    emat <- plot_evaluate_by_true_rank4(data_list, rdasim = sim, size = size, n_iterations)
    
    # Store as matrix
    emat_list[[as.character(size)]] <- as.matrix(emat)

  }
combined_emat <- list()

for (k_name in rownames(emat_list$large)) {
  combined_emat[[k_name]] <- list()
  
  method_names <- names(emat_list$large[k_name, ][[1]])
  
  for (method in method_names) {
    vec_large <- emat_list$large[k_name, ][[1]][[method]]
    vec_small <- emat_list$small[k_name, ][[1]][[method]]
    combined_vec <- c(vec_small, vec_large)

    combined_emat[[k_name]][[method]] <- combined_vec
  }
}

# Prepare summary data frame
summary_df <- data.frame()

for (k_name in names(combined_emat)) {
  for (method in names(combined_emat[[k_name]])) {
    values <- combined_emat[[k_name]][[method]]
    n <- length(values)
    mean_val <- round(mean(values, na.rm = TRUE),2)
    se_val <- round(sd(values, na.rm = TRUE) / sqrt(n),2)

    summary_df <- rbind(summary_df, data.frame(
      Method = method,
      k = k_name,
      Mean = mean_val,
      SE = se_val
    ))
  }
}

# Convert to wide format
mean_table <- summary_df %>%
  select(Method, k, Mean) %>%
  pivot_wider(names_from = k, values_from = Mean)

se_table <- summary_df %>%
  select(Method, k, SE) %>%
  pivot_wider(names_from = k, values_from = SE)

# Add Overall column
mean_table$Overall <- round(rowMeans(mean_table[,-1], na.rm = TRUE),2)
se_table$Overall <- round(rowMeans(se_table[,-1], na.rm = TRUE),2)

# Display results
print(mean_table[,c(1:4)])
print(se_table[,c(1:4)])
}


```



```{r}

for (sim in simulations) {
  #cat("Simulation:", sim, "\n")
  
  emat_list <- list()  # List to store emat for each size
  
  for (size in sizes) {
    #cat("Size:", size, "\n")
    
    filename <- paste0("data_list50_", sim, "_", size, "_all200.rds")
    data_list <- readRDS(here(dir_path, filename))
    
    # Compute accuracy matrix
    emat <- plot_evaluate_by_true_rank4(data_list, rdasim = sim, size = size, n_iterations)
    
    # Store as matrix
    emat_list[[as.character(size)]] <- as.matrix(emat)

  }
combined_emat <- list()

for (k_name in rownames(emat_list$large)) {
  combined_emat[[k_name]] <- list()
  
  method_names <- names(emat_list$large[k_name, ][[1]])
  
  for (method in method_names) {
    vec_large <- emat_list$large[k_name, ][[1]][[method]]
    vec_small <- emat_list$small[k_name, ][[1]][[method]]
    combined_vec <- c(vec_small, vec_large)

    combined_emat[[k_name]][[method]] <- combined_vec
  }
}


combo <- expand.grid(
  n = c(100,200),
  pq = c(50, 100, 200,500),
  k = c(2, 5, 10)
)

results_df <- combo
method_names <- names(combined_emat[[1]])

for (k_name in names(combined_emat)) {
  k_val <- as.numeric(sub("k=", "", k_name))
  combo_idx <- which(combo$k == k_val)
  n_combo_k <- length(combo_idx)

  for (method in method_names) {
    values <- combined_emat[[k_name]][[method]]

    mat <- matrix(values, nrow = n_iterations, ncol =n_combo_k , byrow = FALSE)

    # 平均と SE を計算
    mean_vals <- colMeans(mat)
    se_vals <- round(apply(mat, 2, sd) / sqrt(n_iterations),2)

    # 列名を設定
    mean_colname <- paste0(method, "_mean")
    se_colname <- paste0(method, "_se")

    # 必要なら列を初期化
    if (!mean_colname %in% colnames(results_df)) {
      results_df[[mean_colname]] <- NA
    }
    if (!se_colname %in% colnames(results_df)) {
      results_df[[se_colname]] <- NA
    }

    # 結果を代入
    results_df[combo_idx, mean_colname] <- mean_vals
    results_df[combo_idx, se_colname] <- se_vals
  }
}

print(results_df)

saveRDS(results_df,file = here(dir_path, paste0(sim,"rdf200.rds")))

}

```
# table
```{r}

print("s2n 01")
dir_path<- here("out/eval_01")
mod<-c("Model 1","Model 2")


all_results <- list()
i=1
for (sim in simulations) {
  a<- readRDS( file = here(dir_path, paste0(sim, "rdf200.rds")))
  ar <- readRDS( file = here(dir_path, paste0(sim, "rdf200_rrda.rds")))[,c(4:5)]
  #ac <- readRDS( file = here(dir_path, paste0(sim, "rdf200naive_cv.rds")))
  ac <- readRDS( file = here(dir_path, paste0(sim, "rdf200naive.rds")))[,c(1:3,14,15)]
  a<-cbind(a,ac,ar)
  a <- a[, c(1:13, 16, 17,21:24 )]
  a$sim <- mod[i] 
  all_results[[sim]] <- a
    i<-i+1
}

combined <- do.call(rbind, all_results)
combined <- combined[, c(ncol(combined), 1:(ncol(combined)-1))]
num_cols <- ncol(combined)
digits_vec <- c(0, 0, 0, 0,0, rep(2, num_cols - 4))
addtorow <- list()
addtorow$pos <- list(24)
addtorow$command <- "\\midrule \n"

print(
  xtable(combined, digits = digits_vec),
  include.rownames = FALSE,
  add.to.row = addtorow,
  booktabs = TRUE  # \midrule を使うためには必要
)

print("s2n 1")
dir_path<- here("out/eval_1")



all_results <- list()
i=1
for (sim in simulations) {
  a<- readRDS( file = here(dir_path, paste0(sim, "rdf200.rds")))
  ar <- readRDS( file = here(dir_path, paste0(sim, "rdf200_rrda.rds")))[,c(4:5)]
  #ac <- readRDS( file = here(dir_path, paste0(sim, "rdf200naive_cv.rds")))
  ac <- readRDS( file = here(dir_path, paste0(sim, "rdf200naive.rds")))[,c(1:3,14,15)]
  a<-cbind(a,ac,ar)
  a <- a[, c(1:13, 16, 17,21:24 )]
  a$sim <- mod[i] 
  all_results[[sim]] <- a
    i<-i+1
}
combined <- do.call(rbind, all_results)
combined <- combined[, c(ncol(combined), 1:(ncol(combined)-1))]
num_cols <- ncol(combined)
digits_vec <- c(0, 0, 0, 0,0, rep(2, num_cols - 4))
addtorow <- list()
addtorow$pos <- list(24)
addtorow$command <- "\\midrule \n"

print(
  xtable(combined, digits = digits_vec),
  include.rownames = FALSE,
  add.to.row = addtorow,
  booktabs = TRUE  # \midrule を使うためには必要
)
print("s2n 10")
dir_path<- here("out/eval_10")


all_results <- list()
i=1
for (sim in simulations) {
  a<- readRDS( file = here(dir_path, paste0(sim, "rdf200.rds")))
  ar <- readRDS( file = here(dir_path, paste0(sim, "rdf200_rrda.rds")))[,c(4:5)]
  #ac <- readRDS( file = here(dir_path, paste0(sim, "rdf200naive_cv.rds")))
  ac <- readRDS( file = here(dir_path, paste0(sim, "rdf200naive.rds")))[,c(1:3,14,15)]
  a<-cbind(a,ac,ar)
  a <- a[, c(1:13, 16, 17,21:24 )]
  a$sim <- mod[i] 
  all_results[[sim]] <- a
    i<-i+1
}
combined <- do.call(rbind, all_results)
combined <- combined[, c(ncol(combined), 1:(ncol(combined)-1))]
num_cols <- ncol(combined)
digits_vec <- c(0, 0, 0, 0,0, rep(2, num_cols - 4))

addtorow <- list()
addtorow$pos <- list(24)
addtorow$command <- "\\midrule \n"

print(
  xtable(combined, digits = digits_vec),
  include.rownames = FALSE,
  add.to.row = addtorow,
  booktabs = TRUE  # \midrule を使うためには必要
)
```


```{r}
simulations <- c("sim1","sim2")

print("s2n 01")
dir_path<- here("out/eval_01")
mod<-c("Model1","Model2")

all_results <- list()
i=1
for (sim in simulations) {
  a<- readRDS( file = here(dir_path, paste0(sim, "rdf200.rds")))
  ar <- readRDS(file = here(dir_path, paste0(sim, "rdf200_rrda.rds")))[,c(4:5)]
  #ac <- readRDS(file = here(dir_path, paste0(sim, "rdf200naive_cv.rds")))
  ac <- readRDS( file = here(dir_path, paste0(sim, "rdf200naive.rds")))[,c(1:3,14,15)]
  a<-cbind(a,ac,ar)
  a <- a[, c(1:13, 16, 17,21:24 )]
  
  a$sim <- mod[i] 
  all_results[[sim]] <- a
    i<-i+1
}


combined <- do.call(rbind, all_results)
combined <- combined[, c(ncol(combined), 1:(ncol(combined)-1))]
num_cols <- ncol(combined)

combined<-combined[c(5,13,21,29,37,45),]


digits_vec <- c(0, 0, 0, 0,0, rep(2, num_cols - 4))

print(
  xtable(combined, digits = digits_vec),
  include.rownames = FALSE,
  booktabs = TRUE  # \midrule を使うためには必要
)

print("s2n 1")
dir_path<- here("out/eval_1")
mod<-c("Model1","Model2")
all_results <- list()
i=1
for (sim in simulations) {
  a<- readRDS( file = here(dir_path, paste0(sim, "rdf200.rds")))
  ar <- readRDS( file = here(dir_path, paste0(sim, "rdf200_rrda.rds")))[,c(4:5)]
  #ac <- readRDS( file = here(dir_path, paste0(sim, "rdf200naive_cv.rds")))
  ac <- readRDS( file = here(dir_path, paste0(sim, "rdf200naive.rds")))[,c(1:3,14,15)]
  a<-cbind(a,ac,ar)
  a <- a[, c(1:13, 16, 17,21:24 )]
  
  a$sim <- mod[i] 
  all_results[[sim]] <- a
    i<-i+1
}



combined <- do.call(rbind, all_results)
combined <- combined[, c(ncol(combined), 1:(ncol(combined)-1))]
num_cols <- ncol(combined)

combined<-combined[c(5,13,21,29,37,45),]


digits_vec <- c(0, 0, 0, 0,0, rep(2, num_cols - 4))

print(
  xtable(combined, digits = digits_vec),
  include.rownames = FALSE,
  booktabs = TRUE  # \midrule を使うためには必要
)



print("s2n 10")
dir_path<- here("out/eval_10")
mod<-c("Model1","Model2")
all_results <- list()
i=1
for (sim in simulations) {
  a<- readRDS( file = here(dir_path, paste0(sim, "rdf200.rds")))
  ar <- readRDS( file = here(dir_path, paste0(sim, "rdf200_rrda.rds")))[,c(4:5)]
  #ac <- readRDS( file = here(dir_path, paste0(sim, "rdf200naive_cv.rds")))
  ac <- readRDS( file = here(dir_path, paste0(sim, "rdf200naive.rds")))[,c(1:3,14,15)]
  a<-cbind(a,ac,ar)
  a <- a[, c(1:13, 16, 17,21:24 )]
  
  a$sim <- mod[i] 
  all_results[[sim]] <- a
    i<-i+1
}


combined <- do.call(rbind, all_results)
combined <- combined[, c(ncol(combined), 1:(ncol(combined)-1))]
num_cols <- ncol(combined)

combined<-combined[c(5,13,21,29,37,45),]


digits_vec <- c(0, 0, 0, 0,0, rep(2, num_cols - 4))

print(
  xtable(combined, digits = digits_vec),
  include.rownames = FALSE,
  booktabs = TRUE  # \midrule を使うためには必要
)

```

```{r,warning=T}
library(xtable)
library(here)

# ノイズレベル（ディレクトリ名と表示用s2n値）
s2n_levels <- c("01", "1", "10")
s2n_labels <- c("0.1", "1", "10")
mod <- c("Model1", "Model2")
simulations <- c("sim1", "sim2")  # 適宜シミュレーション名に変更
results_list <- list()

# --- 各s2nディレクトリからデータを収集 ---
for (i_s2n in seq_along(s2n_levels)) {
  s2n <- s2n_levels[i_s2n]
  dir_path <- here(paste0("out/eval_", s2n))
all_results <- list()
i=1
for (sim in simulations) {
  a<- readRDS( file = here(dir_path, paste0(sim, "rdf200.rds")))
  ar <- readRDS( file = here(dir_path, paste0(sim, "rdf200_rrda.rds")))[,c(4:5)]
  #ac <- readRDS( file = here(dir_path, paste0(sim, "rdf200naive_cv.rds")))
  ac <- readRDS( file = here(dir_path, paste0(sim, "rdf200naive.rds")))[,c(1:3,14,15)]
  a<-cbind(a,ac,ar)
  a <- a[, c(1:13, 16, 17,21:24 )]
  
  a$sim <- mod[i] 
  all_results[[sim]] <- a
    i<-i+1
}

  combined <- do.call(rbind, all_results)
  combined <- combined[, c(ncol(combined), 1:(ncol(combined)-1))]
  combined <- combined[c(5,13,21,29,37,45), ]  # 特定の行のみ抽出
  combined$s2n <- s2n_labels[i_s2n]
  results_list[[i_s2n]] <- combined
}

# 全て結合
final_table <- do.call(rbind, results_list)

# --- LaTeXテーブルとして出力 ---
cat("\\begin{tabular}{lcl|cccccccc}\n")
cat("    \\toprule\n")
cat("    \\textbf{s2n} & \\textbf{Model} & \\textbf{rank ($k$)} & \\textbf{ANN.AIC} & \\textbf{ANN.BIC} & \\textbf{ANN.GIC} & \\textbf{ANN.BICP} & \\textbf{ANN.GCV} & \\textbf{StARS} & \\textbf{RRR.CV} & \\textbf{rrda.cv} \\\\\n")
cat("    \\midrule\n")

row_idx <- 1
for (i_s2n in seq_along(s2n_labels)) {
  s2n_group <- results_list[[i_s2n]]
  cat(sprintf("    \\multirow{6}{*}{\\textbf{%s}} \n", s2n_labels[i_s2n]))
  for (model in mod) {
    model_group <- s2n_group[s2n_group$sim == model, ]
    for (j in 1:nrow(model_group)) {
      row <- model_group[j, ]
      prefix <- if (j == 1 && model == mod[1]) "        & \\multirow{3}{*}{Model 1}" else if (j == 1 && model == mod[2]) "        & \\multirow{3}{*}{Model 2}" else "        &"
      line <- sprintf("%s & %2d & %.2f (%.2f) & %.2f (%.2f) & %.2f (%.2f) & %.2f (%.2f) & %.2f (%.2f) & %.2f (%.2f) & %.2f (%.2f) & %.2f (%.2f) \\\\",
                prefix, row$k,
                row$AIC_mean, row$AIC_se,
                row$BIC_mean, row$BIC_se,
                row$GIC_mean, row$GIC_se,
                row$BICP_mean, row$BICP_se,
                row$GCV_mean, row$GCV_se,
                row$StARS_mean, row$StARS_se,
                row$CV_mean, row$CV_se,        # ← RRR.CV
                row$rrda_mean, row$rrda_se)    # ← rrda.cv
      cat(line, "\n")
    }
  }
  if (i_s2n < length(s2n_labels)) cat("    \\midrule\n")
}
cat("    \\bottomrule\n")
cat("\\end{tabular}\n")

```



# session info
check the info and environment
```{r}
devtools::session_info()
```
