---
title: "Senario 2-2 : Rank Estimate Evaluation on Simulation Data with RRDA (different noise parameters)"
output: html_document
author: "Hayato Yoshioka (University of Tokyo, AgroParisTech)"
---

# package
```{r}
library(furrr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(RSpectra)
library(rrda)
library(xtable)
library(purrr) 
library(here)
library(progress)
source("script_rrda/functions_rrda_yoshioka.R")
source("script_rrda/functions_stars_rrr_yoshioka.R")
library(furrr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(RSpectra)
library(rrda)
library(here)
library(xtable)
library(pheatmap)
library(tictoc)
library(tidyr)
library(tibble)
library(here)
library(xtable)
library(rrpack)
```

#1
Create the folder for saving
```{r}
dir_path<- here("out/eval_1")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
}

```

```{r}
rdasim1<- function(n,p,q,k,s2n = c(1, 1)){
  H  <- matrix(stats::rnorm(n = n*k, mean = 0, sd = 1),n,k)
  
  theta.x  <- matrix(stats::rnorm(n = k*p, mean = 0, sd = 1),k,p)
  noise.x <-  matrix(stats::rnorm(n = n*p, mean = 0, sd = 1),n,p)
  
  signal.x <- H %*% theta.x
  sigma.x <- sqrt(sum(signal.x^2) / (sum(noise.x^2) * s2n[1]))
  noise.x <- sigma.x * noise.x

  X  <- signal.x + noise.x
  
  theta.y  <- matrix(stats::rnorm(n = k*q, mean = 0, sd = 1),k,q)
  noise.y  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  
  signal.y <- H %*% theta.y
  sigma.y <- sqrt(sum(signal.y^2) / (sum(noise.y^2) * s2n[2]))
  noise.y <- sigma.y * noise.y


  Y  <- signal.y + noise.y

  return(list(X=X,Y=Y,H=H,theta.y=theta.y))
}

rdasim2<- function(n,p,q,k,s2n=1,xofd=0){
  cov <- matrix(xofd, nrow = p, ncol = p)
  diag(cov) <- 1
  X  <- MASS::mvrnorm(n, rep(0, p), cov)

  A <- matrix(stats::rnorm(n = p * k, mean = 0, sd = 1), p, k)
  A <- apply(A, 2, function(col) col / sqrt(sum(col^2)))
  C <- matrix(stats::rnorm(n = k * q, mean = 0, sd = 1), k, q)
  C <- apply(C, 2, function(col) col / sqrt(sum(col^2)))

  B  <- crossprod(t(A),C)
  E  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  XB <- crossprod(t(X),B)
  sigma <- sqrt(sum(XB^2) / (sum(E^2) * s2n))
  E  <- E * sigma
  Y <- XB + E
  return(list(X=X,Y=Y,B=B,E=E))
}


```

# simulation run 
2 types of simulations and 2 size of n, 3 size of p and q, 3 size of r

```{r}
set.seed(123)

n_iterations=20
# Define your conditions
simulations <- c("sim1","sim2")
sizes <- c("large", "small")


simulations <- c("sim2")
sizes <- c("large")

# Loop over each combination
for (sim in simulations) {

  for (size in sizes) {
    # Run your function with each combination
    data_list <- rank_evaluate_50_allcriteria(n_iterations = n_iterations, rdasim = sim, size = size)
    # Save the results
    filename <- paste0("data_list50_", sim, "_", size, "_all.rds")
    saveRDS(data_list, file = here(dir_path, filename))
    data_list<-readRDS(here(dir_path, filename))
    pp<-plot_evaluate_all(data_list,rdasim = sim,size=size,n_iterations)
    pp
  }
}

```

# get result
Plot the results
```{r,warning=FALSE}
set.seed(123)
n_iterations=20
# Define your conditions
 simulations <- c("sim1", "sim2")
 sizes <- c("large", "small")
 #simulations <- c("sim1")
 #sizes <- c( "small")

for (sim in simulations) {

	print(sim)
  for (size in sizes) {
  	print(size)
  	filename <- paste0("data_list50_", sim, "_", size, "_all.rds")
		data_list<-readRDS(here(dir_path, filename))
    pp<-plot_evaluate_all(data_list,rdasim = sim,size=size,n_iterations)
    plot_evaluate_by_true_rank(data_list,rdasim = sim,size=size,n_iterations)
    emat<-plot_evaluate_by_true_rank2(data_list,rdasim = sim,size=size,n_iterations)
    #plot_all(data_list,rdasim = sim,size=size,n_iterations)
    data_list$perR_vec<-pp$perR_vec
  }
	
}
 
for (sim in simulations) {
  cat("Simulation:", sim, "\n")
  
  emat_list <- list()  # List to store emat for each size
  
  for (size in sizes) {
    cat("Size:", size, "\n")
    
    filename <- paste0("data_list50_", sim, "_", size, "_all.rds")
    data_list <- readRDS(here(dir_path, filename))
    
    # Compute accuracy matrix
    emat <- plot_evaluate_by_true_rank2(data_list, rdasim = sim, size = size, n_iterations)
    
    # Store as matrix
    emat_list[[as.character(size)]] <- as.matrix(emat)
  }
  
  # Compute average across sizes
  mean_emat <- Reduce("+", emat_list) / length(emat_list)
  mean_emat_df <- as.data.frame(round(mean_emat, 1))
  
  # Output result
  cat("Average accuracy for simulation:", sim, "\n")
  print(mean_emat_df)
  
  # Optional: save result
  # write.csv(mean_emat_df, paste0("mean_accuracy_", sim, ".csv"), row.names = TRUE)
}

```

```{r}
set.seed(123)
# Define your conditions
 simulations <- c("sim1", "sim2")
 #simulations <- c("sim1")
 sizes <- c("large", "small")

for (sim in simulations) {

  for (size in sizes) {
  	filename <- paste0("data_list50_", sim, "_", size, "_all.rds")
		data_list<-readRDS(here(dir_path, filename))
    pp<-plot_evaluate_all(data_list,rdasim = sim,size=size,n_iterations)
    results_list <- data_list$esR_vector
    methods<-names(results_list[[1]])
    for (method in methods) {
    	print(method)
    #data_list$perR_vec <- pp[[method]]$perR_vec
    
	if (size == "small") {
  combo <- expand.grid(
    n = c(100, 200),
    pq = c(50, 100),
    k = c(2, 5, 10)
  )
} else if (size == "large") {
  combo <- expand.grid(
    n = c(100, 200),
    pq = c(500, 1000),
    k = c(2, 5, 10)
  )
}
    combo$Match <- pp[[method]]$perR_vec
    print(combo)
    }
  }
}
```



#10
Create the folder for saving
```{r}
dir_path<- here("out/eval_10")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
}

```



```{r}
rdasim1<- function(n,p,q,k,s2n = c(10, 10)){
  H  <- matrix(stats::rnorm(n = n*k, mean = 0, sd = 1),n,k)
  
  theta.x  <- matrix(stats::rnorm(n = k*p, mean = 0, sd = 1),k,p)
  noise.x <-  matrix(stats::rnorm(n = n*p, mean = 0, sd = 1),n,p)
  
  signal.x <- H %*% theta.x
  sigma.x <- sqrt(sum(signal.x^2) / (sum(noise.x^2) * s2n[1]))
  noise.x <- sigma.x * noise.x

  X  <- signal.x + noise.x
  
  theta.y  <- matrix(stats::rnorm(n = k*q, mean = 0, sd = 1),k,q)
  noise.y  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  
  signal.y <- H %*% theta.y
  sigma.y <- sqrt(sum(signal.y^2) / (sum(noise.y^2) * s2n[2]))
  noise.y <- sigma.y * noise.y


  Y  <- signal.y + noise.y

  return(list(X=X,Y=Y,H=H,theta.y=theta.y))
}

rdasim2<- function(n,p,q,k,s2n=10,xofd=0){
  cov <- matrix(xofd, nrow = p, ncol = p)
  diag(cov) <- 1
  X  <- MASS::mvrnorm(n, rep(0, p), cov)

  A <- matrix(stats::rnorm(n = p * k, mean = 0, sd = 1), p, k)
  A <- apply(A, 2, function(col) col / sqrt(sum(col^2)))
  C <- matrix(stats::rnorm(n = k * q, mean = 0, sd = 1), k, q)
  C <- apply(C, 2, function(col) col / sqrt(sum(col^2)))

  B  <- crossprod(t(A),C)
  E  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  XB <- crossprod(t(X),B)
  sigma <- sqrt(sum(XB^2) / (sum(E^2) * s2n))
  E  <- E * sigma
  Y <- XB + E
  return(list(X=X,Y=Y,B=B,E=E))
}


```


# simulation run 
2 types of simulations and 2 size of n, 3 size of p and q, 3 size of r

```{r}
set.seed(123)

n_iterations=20
# Define your conditions
simulations <- c("sim1","sim2")
sizes <- c("large", "small")

#simulations <- c("sim1")
#sizes <- c("small")

# Loop over each combination
for (sim in simulations) {

  for (size in sizes) {
    # Run your function with each combination
    data_list <- rank_evaluate_50_allcriteria(n_iterations = n_iterations, rdasim = sim, size = size)
    # Save the results
    filename <- paste0("data_list50_", sim, "_", size, "_all.rds")
    saveRDS(data_list, file = here(dir_path, filename))
    data_list<-readRDS(here(dir_path, filename))
    pp<-plot_evaluate_all(data_list,rdasim = sim,size=size,n_iterations)
    pp
  }
}

```

# get result
Plot the results
```{r,warning=FALSE}
set.seed(123)
n_iterations=20
# Define your conditions
 simulations <- c("sim1", "sim2")
 sizes <- c("large", "small")
 #simulations <- c("sim1")
 #sizes <- c( "small")

for (sim in simulations) {

	print(sim)
  for (size in sizes) {
  	print(size)
  	filename <- paste0("data_list50_", sim, "_", size, "_all.rds")
		data_list<-readRDS(here(dir_path, filename))
    pp<-plot_evaluate_all(data_list,rdasim = sim,size=size,n_iterations)
    plot_evaluate_by_true_rank(data_list,rdasim = sim,size=size,n_iterations)
    emat<-plot_evaluate_by_true_rank2(data_list,rdasim = sim,size=size,n_iterations)
    #plot_all(data_list,rdasim = sim,size=size,n_iterations)
    data_list$perR_vec<-pp$perR_vec
  }
	
}
 
for (sim in simulations) {
  cat("Simulation:", sim, "\n")
  
  emat_list <- list()  # List to store emat for each size
  
  for (size in sizes) {
    cat("Size:", size, "\n")
    
    filename <- paste0("data_list50_", sim, "_", size, "_all.rds")
    data_list <- readRDS(here(dir_path, filename))
    
    # Compute accuracy matrix
    emat <- plot_evaluate_by_true_rank2(data_list, rdasim = sim, size = size, n_iterations)
    
    # Store as matrix
    emat_list[[as.character(size)]] <- as.matrix(emat)
  }
  
  # Compute average across sizes
  mean_emat <- Reduce("+", emat_list) / length(emat_list)
  mean_emat_df <- as.data.frame(round(mean_emat, 1))
  
  # Output result
  cat("Average accuracy for simulation:", sim, "\n")
  print(mean_emat_df)
  
  # Optional: save result
  # write.csv(mean_emat_df, paste0("mean_accuracy_", sim, ".csv"), row.names = TRUE)
}

```

```{r}
set.seed(123)
# Define your conditions
 simulations <- c("sim1", "sim2")
 #simulations <- c("sim1")
 sizes <- c("large", "small")

for (sim in simulations) {

  for (size in sizes) {
  	filename <- paste0("data_list50_", sim, "_", size, "_all.rds")
		data_list<-readRDS(here(dir_path, filename))
    pp<-plot_evaluate_all(data_list,rdasim = sim,size=size,n_iterations)
    results_list <- data_list$esR_vector
    methods<-names(results_list[[1]])
    for (method in methods) {
    	print(method)
    #data_list$perR_vec <- pp[[method]]$perR_vec
    
	if (size == "small") {
  combo <- expand.grid(
    n = c(100, 200),
    pq = c(50, 100),
    k = c(2, 5, 10)
  )
} else if (size == "large") {
  combo <- expand.grid(
    n = c(100, 200),
    pq = c(500, 1000),
    k = c(2, 5, 10)
  )
}
    combo$Match <- pp[[method]]$perR_vec
    print(combo)
    }
  }
}
```


#01
Create the folder for saving
```{r}
dir_path<- here("out/eval_01")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
}

```


```{r}
rdasim1<- function(n,p,q,k,s2n = c(0.1, 0.1)){
  H  <- matrix(stats::rnorm(n = n*k, mean = 0, sd = 1),n,k)
  
  theta.x  <- matrix(stats::rnorm(n = k*p, mean = 0, sd = 1),k,p)
  noise.x <-  matrix(stats::rnorm(n = n*p, mean = 0, sd = 1),n,p)
  
  signal.x <- H %*% theta.x
  sigma.x <- sqrt(sum(signal.x^2) / (sum(noise.x^2) * s2n[1]))
  noise.x <- sigma.x * noise.x

  X  <- signal.x + noise.x
  
  theta.y  <- matrix(stats::rnorm(n = k*q, mean = 0, sd = 1),k,q)
  noise.y  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  
  signal.y <- H %*% theta.y
  sigma.y <- sqrt(sum(signal.y^2) / (sum(noise.y^2) * s2n[2]))
  noise.y <- sigma.y * noise.y


  Y  <- signal.y + noise.y

  return(list(X=X,Y=Y,H=H,theta.y=theta.y))
}

rdasim2<- function(n,p,q,k,s2n=0.1,xofd=0){
  cov <- matrix(xofd, nrow = p, ncol = p)
  diag(cov) <- 1
  X  <- MASS::mvrnorm(n, rep(0, p), cov)

  A <- matrix(stats::rnorm(n = p * k, mean = 0, sd = 1), p, k)
  A <- apply(A, 2, function(col) col / sqrt(sum(col^2)))
  C <- matrix(stats::rnorm(n = k * q, mean = 0, sd = 1), k, q)
  C <- apply(C, 2, function(col) col / sqrt(sum(col^2)))

  B  <- crossprod(t(A),C)
  E  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  XB <- crossprod(t(X),B)
  sigma <- sqrt(sum(XB^2) / (sum(E^2) * s2n))
  E  <- E * sigma
  Y <- XB + E
  return(list(X=X,Y=Y,B=B,E=E))
}


```

# simulation run 
2 types of simulations and 2 size of n, 3 size of p and q, 3 size of r

```{r}
set.seed(123)

n_iterations=20
# Define your conditions
simulations <- c("sim1","sim2")
sizes <- c("large", "small")

#simulations <- c("sim1")
#sizes <- c("small")

# Loop over each combination
for (sim in simulations) {

  for (size in sizes) {
    # Run your function with each combination
    data_list <- rank_evaluate_50_allcriteria(n_iterations = n_iterations, rdasim = sim, size = size)
    # Save the results
    filename <- paste0("data_list50_", sim, "_", size, "_all.rds")
    saveRDS(data_list, file = here(dir_path, filename))
    data_list<-readRDS(here(dir_path, filename))
    pp<-plot_evaluate_all(data_list,rdasim = sim,size=size,n_iterations)
    pp
  }
}

```

# get result
Plot the results
```{r,warning=FALSE}
set.seed(123)
n_iterations=20
# Define your conditions
 simulations <- c("sim1", "sim2")
 sizes <- c("large", "small")
 #simulations <- c("sim1")
 #sizes <- c( "small")

for (sim in simulations) {

	print(sim)
  for (size in sizes) {
  	print(size)
  	filename <- paste0("data_list50_", sim, "_", size, "_all.rds")
		data_list<-readRDS(here(dir_path, filename))
    pp<-plot_evaluate_all(data_list,rdasim = sim,size=size,n_iterations)
    plot_evaluate_by_true_rank(data_list,rdasim = sim,size=size,n_iterations)
    emat<-plot_evaluate_by_true_rank2(data_list,rdasim = sim,size=size,n_iterations)
    #plot_all(data_list,rdasim = sim,size=size,n_iterations)
    data_list$perR_vec<-pp$perR_vec
  }
	
}
 
for (sim in simulations) {
  cat("Simulation:", sim, "\n")
  
  emat_list <- list()  # List to store emat for each size
  
  for (size in sizes) {
    cat("Size:", size, "\n")
    
    filename <- paste0("data_list50_", sim, "_", size, "_all.rds")
    data_list <- readRDS(here(dir_path, filename))
    
    # Compute accuracy matrix
    emat <- plot_evaluate_by_true_rank2(data_list, rdasim = sim, size = size, n_iterations)
    
    # Store as matrix
    emat_list[[as.character(size)]] <- as.matrix(emat)
  }
  
  # Compute average across sizes
  mean_emat <- Reduce("+", emat_list) / length(emat_list)
  mean_emat_df <- as.data.frame(round(mean_emat, 1))
  
  # Output result
  cat("Average accuracy for simulation:", sim, "\n")
  print(mean_emat_df)
  
  # Optional: save result
  # write.csv(mean_emat_df, paste0("mean_accuracy_", sim, ".csv"), row.names = TRUE)
}

```

```{r}
set.seed(123)
# Define your conditions
 simulations <- c("sim1", "sim2")
 #simulations <- c("sim1")
 sizes <- c("large", "small")

for (sim in simulations) {

  for (size in sizes) {
  	filename <- paste0("data_list50_", sim, "_", size, "_all.rds")
		data_list<-readRDS(here(dir_path, filename))
    pp<-plot_evaluate_all(data_list,rdasim = sim,size=size,n_iterations)
    results_list <- data_list$esR_vector
    methods<-names(results_list[[1]])
    for (method in methods) {
    	print(method)
    #data_list$perR_vec <- pp[[method]]$perR_vec
    
	if (size == "small") {
  combo <- expand.grid(
    n = c(100, 200),
    pq = c(50, 100),
    k = c(2, 5, 10)
  )
} else if (size == "large") {
  combo <- expand.grid(
    n = c(100, 200),
    pq = c(500, 1000),
    k = c(2, 5, 10)
  )
}
    combo$Match <- pp[[method]]$perR_vec
    print(combo)
    }
  }
}
```


# all data table
```{}
set.seed(123)
n_iterations <- 50
simulations <- c("sim1", "sim2")
sizes <- c("large", "small")
s2n_levels <- c("0.1", "1", "10")
s2n_dirs <- c("0.1" = "eval_01", "1" = "eval_1", "10" = "eval_10")

# 結果格納用リスト
all_results <- list()

for (size in sizes) {
  # パラメータ組み合わせ（sizeごと）
  combo <- if (size == "small") {
    expand.grid(
      n = c(100, 200),
      pq = c(50, 100),
      k = c(2, 5, 10)
    )
  } else {
    expand.grid(
      n = c(100, 200),
      pq = c(500, 1000),
      k = c(2, 5, 10)
    )
  }

  combo$size <- size

  # 各 sim × s2n に対応する Match 列を追加
  for (sim in simulations) {
    for (s2n in s2n_levels) {
      dir_path <- here("out", s2n_dirs[[s2n]])
      filename <- paste0("data_list50_", sim, "_", size, ".rds")
      full_path <- file.path(dir_path, filename)

      if (file.exists(full_path)) {
        data_list <- readRDS(full_path)
        pp <- plot_evaluate(data_list, rdasim = sim, size = size, n_iterations = n_iterations)
        combo[[paste0("Match (s2n=", s2n, ", ", sim, ")")]] <- pp$perR_vec
      } else {
        warning("File not found: ", full_path)
        combo[[paste0("Match (s2n=", s2n, ", ", sim, ")")]] <- NA
      }
    }
  }

  all_results[[length(all_results) + 1]] <- combo
}

# すべてまとめる
final_table <- bind_rows(all_results) %>%
  relocate(size, n, pq, k)

# 表示
print(final_table)


```


```{}

colnames(final_table) <- gsub("Match \\(s2n=([0-9.]+), (sim[0-9])\\)", "Match (\\1, \\2)", colnames(final_table))

# xtable
latex_table <- xtable(final_table, digits = 2, caption = "Rank estimation accuracy across simulation settings (Match rates).", label = "tab:match_rates")

# LaTeX
print(latex_table, include.rownames = FALSE, sanitize.text.function = identity)

```


# session info
check the info and environment
```{r}
devtools::session_info()
```
