---
title: "Senario 3-2 : Random Splitting Process on Simulation Data with RRDA (different noise parameters)"
output: html_document
author: "Hayato Yoshioka (University of Tokyo, AgroParisTech)"
---

# package
```{r}
library(furrr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(RSpectra)
library(rrda)
library(here)
library(xtable)
library(pheatmap)
library(tictoc)
source("script_rrda/functions_rrda_yoshioka.R")
source("script_rrda/functions_stars_rrr_yoshioka.R")
```

Create the folder for saving

# 1
```{r}
rdasim1<- function(n,p,q,k,s2n = c(1, 1)){
  H  <- matrix(stats::rnorm(n = n*k, mean = 0, sd = 1),n,k)
  
  theta.x  <- matrix(stats::rnorm(n = k*p, mean = 0, sd = 1),k,p)
  noise.x <-  matrix(stats::rnorm(n = n*p, mean = 0, sd = 1),n,p)
  
  signal.x <- H %*% theta.x
  sigma.x <- sqrt(sum(signal.x^2) / (sum(noise.x^2) * s2n[1]))
  noise.x <- sigma.x * noise.x

  X  <- signal.x + noise.x
  
  theta.y  <- matrix(stats::rnorm(n = k*q, mean = 0, sd = 1),k,q)
  noise.y  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  
  signal.y <- H %*% theta.y
  sigma.y <- sqrt(sum(signal.y^2) / (sum(noise.y^2) * s2n[2]))
  noise.y <- sigma.y * noise.y


  Y  <- signal.y + noise.y

  return(list(X=X,Y=Y,H=H,theta.y=theta.y))
}

rdasim2<- function(n,p,q,k,s2n=1,xofd=0){
  cov <- matrix(xofd, nrow = p, ncol = p)
  diag(cov) <- 1
  X  <- MASS::mvrnorm(n, rep(0, p), cov)

  A <- matrix(stats::rnorm(n = p * k, mean = 0, sd = 1), p, k)
  A <- apply(A, 2, function(col) col / sqrt(sum(col^2)))
  C <- matrix(stats::rnorm(n = k * q, mean = 0, sd = 1), k, q)
  C <- apply(C, 2, function(col) col / sqrt(sum(col^2)))

  B  <- crossprod(t(A),C)
  E  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  XB <- crossprod(t(X),B)
  sigma <- sqrt(sum(XB^2) / (sum(E^2) * s2n))
  E  <- E * sigma
  Y <- XB + E
  return(list(X=X,Y=Y,B=B,E=E))
}

```


# model1
create folders to save
```{r}
base_path <- here("out", "Sim1_1")
dir_path <- file.path(base_path, "aic")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 
```


Generate data
```{r,warning=FALSE}
set.seed(123)
n = 100
p = 200
q = 200
k = 5
simdata<-rdasim1(n = n,p = p,q = q,k = k)
X <- simdata$X
Y <- simdata$Y
```

Define samples to be extracted for Random Splitting process. (100 iterations)
Define the lambda range for each iteration. The lambda and sampling is set to be the same for every parameter tuning criteria.
```{r,eval=F}
set.seed(123)
rn_list <- list()

for (k in 1:100) {
  rn_list[[k]] <- sample(c(1:nrow(X)), 10, replace = FALSE)
}
saveRDS(rn_list,file.path(base_path, "rn_list.RDS"))
lm<-get_lambda_stars(dir_path, rn_list, Y=Y, X=X) 
```

Run the Random Splitting process and get the results
```{r,eval=F}
#base_path <- here("out", "Sim1")
#res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

set.seed(123)

rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))
lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))

Lambda<-rrr_lambda(Y = Y, X = X)
criteria_test_all(Y=Y,X=X,Lambda=Lambda,dir_path=dir_path,maxrank=10)

criteria_test(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)

rsbc_test(Y=Y,X=X,save=dir_path)
tp(save=dir_path)
```


## table
Plot and Table of the results
```{r}
#base_path <- here("out", "Sim1_1")
res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

res<-res[c(1,2,3,4,5,7,6),c(1,4,5,6,7,11,12,8,9)]
res<-t(res)
#res

for (s in c(2,3,5,6,7)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(9)) {
  res[s,]<-rd(res[s,],3)
}

for (s in c(4,7,8)){
	res[s,]<-fd(res[s,],3)
}


for (s in c(3,5,7,9)) {
  res[s, ] <- paste0("(", res[s, ], ")")
}


xtable(res)
res<-readRDS(file.path(base_path,"aic", "criteria_alldata.RDS"))
#res<-res[,c(1,4,5,6,7,11,12,8,9)]
res<-res[c(1,2,3,4,5,7,6),]
res<-t(res)
#res
for (s in c(2)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(3,4)){
	res[s,]<-fd(res[s,],3)
}
#xtable(res)
tp(save=dir_path)

#res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
```


# model2
For the model 2, perform the same procedure.

```{r}
base_path <- here("out", "Sim2_1")
dir_path <- file.path(base_path, "aic")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 
```

Generate data
```{r,warning=FALSE}
set.seed(123)
n = 100
p = 200
q = 200
k = 5
simdata<-rdasim2(n = n,p = p,q = q,k = k,s2n=5)
X <- simdata$X
Y <- simdata$Y
```


```{r,eval=F}
set.seed(123)
rn_list <- list()

for (k in 1:100) {
  rn_list[[k]] <- sample(c(1:nrow(X)), 10, replace = FALSE)
}
saveRDS(rn_list,file.path(base_path, "rn_list.RDS"))
lm<-get_lambda_stars(dir_path, rn_list, Y=Y, X=X) 
```

```{r,eval=F}
set.seed(123)
#base_path <- here("out", "Sim2")
#res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))
lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))

Lambda<-rrr_lambda(Y = Y, X = X)
criteria_test_all(Y=Y,X=X,Lambda=Lambda,dir_path=dir_path,maxrank=10)

criteria_test(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)
#criteria_fit(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)
rsbc_test(Y=Y,X=X,save=dir_path)
tp(save=dir_path)
```

## table
```{r}
#base_path <- here("out", "Sim2")
res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

res<-res[c(1,2,3,4,5,7,6),c(1,4,5,6,7,11,12,8,9)]
res<-t(res)

for (s in c(2,3,5,6,7)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(9)) {
  res[s,]<-rd(res[s,],3)
}

for (s in c(4,7,8)){
	res[s,]<-fd(res[s,],3)
}


for (s in c(3,5,7,9)) {
  res[s, ] <- paste0("(", res[s, ], ")")
}

xtable(res)

res<-readRDS(file.path(base_path,"aic", "criteria_alldata.RDS"))
#res<-res[,c(1,4,5,6,7,11,12,8,9)]
res<-res[c(1,2,3,4,5,7,6),]
res<-t(res)
#res
for (s in c(2)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(3,4)){
	res[s,]<-fd(res[s,],3)
}

#xtable(res)
tp(save=dir_path)
```


# 10


```{r}
rdasim1<- function(n,p,q,k,s2n = c(10, 10)){
  H  <- matrix(stats::rnorm(n = n*k, mean = 0, sd = 1),n,k)
  
  theta.x  <- matrix(stats::rnorm(n = k*p, mean = 0, sd = 1),k,p)
  noise.x <-  matrix(stats::rnorm(n = n*p, mean = 0, sd = 1),n,p)
  
  signal.x <- H %*% theta.x
  sigma.x <- sqrt(sum(signal.x^2) / (sum(noise.x^2) * s2n[1]))
  noise.x <- sigma.x * noise.x

  X  <- signal.x + noise.x
  
  theta.y  <- matrix(stats::rnorm(n = k*q, mean = 0, sd = 1),k,q)
  noise.y  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  
  signal.y <- H %*% theta.y
  sigma.y <- sqrt(sum(signal.y^2) / (sum(noise.y^2) * s2n[2]))
  noise.y <- sigma.y * noise.y


  Y  <- signal.y + noise.y

  return(list(X=X,Y=Y,H=H,theta.y=theta.y))
}

rdasim2<- function(n,p,q,k,s2n=10,xofd=0){
  cov <- matrix(xofd, nrow = p, ncol = p)
  diag(cov) <- 1
  X  <- MASS::mvrnorm(n, rep(0, p), cov)

  A <- matrix(stats::rnorm(n = p * k, mean = 0, sd = 1), p, k)
  A <- apply(A, 2, function(col) col / sqrt(sum(col^2)))
  C <- matrix(stats::rnorm(n = k * q, mean = 0, sd = 1), k, q)
  C <- apply(C, 2, function(col) col / sqrt(sum(col^2)))

  B  <- crossprod(t(A),C)
  E  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  XB <- crossprod(t(X),B)
  sigma <- sqrt(sum(XB^2) / (sum(E^2) * s2n))
  E  <- E * sigma
  Y <- XB + E
  return(list(X=X,Y=Y,B=B,E=E))
}

```


Create the folder for saving
# model1
create folders to save
```{r}
base_path <- here("out", "Sim1_10")
dir_path <- file.path(base_path, "aic")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 
```




Generate data
```{r,warning=FALSE}
set.seed(123)
n = 100
p = 200
q = 200
k = 5
simdata<-rdasim1(n = n,p = p,q = q,k = k)
X <- simdata$X
Y <- simdata$Y
```

Define samples to be extracted for Random Splitting process. (100 iterations)
Define the lambda range for each iteration. The lambda and sampling is set to be the same for every parameter tuning criteria.
```{r,eval=F}
set.seed(123)
rn_list <- list()

for (k in 1:100) {
  rn_list[[k]] <- sample(c(1:nrow(X)), 10, replace = FALSE)
}
saveRDS(rn_list,file.path(base_path, "rn_list.RDS"))
lm<-get_lambda_stars(dir_path, rn_list, Y=Y, X=X) 
```

Run the Random Splitting process and get the results
```{r,eval=F}
#base_path <- here("out", "Sim1")
#res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

set.seed(123)

rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))
lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))

Lambda<-rrr_lambda(Y = Y, X = X)
criteria_test_all(Y=Y,X=X,Lambda=Lambda,dir_path=dir_path,maxrank=10)

criteria_test(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)

rsbc_test(Y=Y,X=X,save=dir_path)
tp(save=dir_path)
```


## table
Plot and Table of the results
```{r}
#base_path <- here("out", "Sim1_1")
res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

res<-res[c(1,2,3,4,5,7,6),c(1,4,5,6,7,11,12,8,9)]
res<-t(res)
#res

for (s in c(2,3,5,6,7)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(9)) {
  res[s,]<-rd(res[s,],3)
}

for (s in c(4,7,8)){
	res[s,]<-fd(res[s,],3)
}


for (s in c(3,5,7,9)) {
  res[s, ] <- paste0("(", res[s, ], ")")
}


xtable(res)
res<-readRDS(file.path(base_path,"aic", "criteria_alldata.RDS"))
#res<-res[,c(1,4,5,6,7,11,12,8,9)]
res<-res[c(1,2,3,4,5,7,6),]
res<-t(res)
#res
for (s in c(2)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(3,4)){
	res[s,]<-fd(res[s,],3)
}
#xtable(res)
tp(save=dir_path)
```


# model2
For the model 2, perform the same procedure.

```{r}
base_path <- here("out", "Sim2_10")
dir_path <- file.path(base_path, "aic")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 
```

Generate data
```{r,warning=FALSE}
set.seed(123)
n = 100
p = 200
q = 200
k = 5
simdata<-rdasim2(n = n,p = p,q = q,k = k,s2n=5)
X <- simdata$X
Y <- simdata$Y
```


```{r,eval=F}
set.seed(123)
rn_list <- list()

for (k in 1:100) {
  rn_list[[k]] <- sample(c(1:nrow(X)), 10, replace = FALSE)
}
saveRDS(rn_list,file.path(base_path, "rn_list.RDS"))
lm<-get_lambda_stars(dir_path, rn_list, Y=Y, X=X) 
```

```{r,eval=F}
set.seed(123)
#base_path <- here("out", "Sim2")
#res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))
lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))

Lambda<-rrr_lambda(Y = Y, X = X)
criteria_test_all(Y=Y,X=X,Lambda=Lambda,dir_path=dir_path,maxrank=10)

criteria_test(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)
#criteria_fit(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)
rsbc_test(Y=Y,X=X,save=dir_path)
tp(save=dir_path)
```

## table
```{r}
#base_path <- here("out", "Sim2")
res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

res<-res[c(1,2,3,4,5,7,6),c(1,4,5,6,7,11,12,8,9)]
res<-t(res)

for (s in c(2,3,5,6,7)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(9)) {
  res[s,]<-rd(res[s,],3)
}

for (s in c(4,7,8)){
	res[s,]<-fd(res[s,],3)
}


for (s in c(3,5,7,9)) {
  res[s, ] <- paste0("(", res[s, ], ")")
}

xtable(res)

res<-readRDS(file.path(base_path,"aic", "criteria_alldata.RDS"))
#res<-res[,c(1,4,5,6,7,11,12,8,9)]
res<-res[c(1,2,3,4,5,7,6),]
res<-t(res)
#res
for (s in c(2)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(3,4)){
	res[s,]<-fd(res[s,],3)
}

#xtable(res)
tp(save=dir_path)
```



# 01


```{r}
rdasim1<- function(n,p,q,k,s2n = c(0.1, 0.1)){
  H  <- matrix(stats::rnorm(n = n*k, mean = 0, sd = 1),n,k)
  
  theta.x  <- matrix(stats::rnorm(n = k*p, mean = 0, sd = 1),k,p)
  noise.x <-  matrix(stats::rnorm(n = n*p, mean = 0, sd = 1),n,p)
  
  signal.x <- H %*% theta.x
  sigma.x <- sqrt(sum(signal.x^2) / (sum(noise.x^2) * s2n[1]))
  noise.x <- sigma.x * noise.x

  X  <- signal.x + noise.x
  
  theta.y  <- matrix(stats::rnorm(n = k*q, mean = 0, sd = 1),k,q)
  noise.y  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  
  signal.y <- H %*% theta.y
  sigma.y <- sqrt(sum(signal.y^2) / (sum(noise.y^2) * s2n[2]))
  noise.y <- sigma.y * noise.y


  Y  <- signal.y + noise.y

  return(list(X=X,Y=Y,H=H,theta.y=theta.y))
}

rdasim2<- function(n,p,q,k,s2n=0.1,xofd=0){
  cov <- matrix(xofd, nrow = p, ncol = p)
  diag(cov) <- 1
  X  <- MASS::mvrnorm(n, rep(0, p), cov)

  A <- matrix(stats::rnorm(n = p * k, mean = 0, sd = 1), p, k)
  A <- apply(A, 2, function(col) col / sqrt(sum(col^2)))
  C <- matrix(stats::rnorm(n = k * q, mean = 0, sd = 1), k, q)
  C <- apply(C, 2, function(col) col / sqrt(sum(col^2)))

  B  <- crossprod(t(A),C)
  E  <- matrix(stats::rnorm(n = n*q, mean = 0, sd = 1),n,q)
  XB <- crossprod(t(X),B)
  sigma <- sqrt(sum(XB^2) / (sum(E^2) * s2n))
  E  <- E * sigma
  Y <- XB + E
  return(list(X=X,Y=Y,B=B,E=E))
}

```


Create the folder for saving
# model1
create folders to save
```{r}
base_path <- here("out", "Sim1_01")
dir_path <- file.path(base_path, "aic")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 
```




Generate data
```{r,warning=FALSE}
set.seed(123)
n = 100
p = 200
q = 200
k = 5
simdata<-rdasim1(n = n,p = p,q = q,k = k)
X <- simdata$X
Y <- simdata$Y
```

Define samples to be extracted for Random Splitting process. (100 iterations)
Define the lambda range for each iteration. The lambda and sampling is set to be the same for every parameter tuning criteria.
```{r,eval=F}
set.seed(123)
rn_list <- list()

for (k in 1:100) {
  rn_list[[k]] <- sample(c(1:nrow(X)), 10, replace = FALSE)
}
saveRDS(rn_list,file.path(base_path, "rn_list.RDS"))
lm<-get_lambda_stars(dir_path, rn_list, Y=Y, X=X) 
```

Run the Random Splitting process and get the results
```{r,eval=F}
#base_path <- here("out", "Sim1")
#res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

set.seed(123)

rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))
lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))

Lambda<-rrr_lambda(Y = Y, X = X)
criteria_test_all(Y=Y,X=X,Lambda=Lambda,dir_path=dir_path,maxrank=10)

criteria_test(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)

rsbc_test(Y=Y,X=X,save=dir_path)
tp(save=dir_path)
```


## table
Plot and Table of the results
```{r}
#base_path <- here("out", "Sim1_1")
res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

res<-res[c(1,2,3,4,5,7,6),c(1,4,5,6,7,11,12,8,9)]
res<-t(res)
#res

for (s in c(2,3,5,6,7)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(9)) {
  res[s,]<-rd(res[s,],3)
}

for (s in c(4,7,8)){
	res[s,]<-fd(res[s,],3)
}


for (s in c(3,5,7,9)) {
  res[s, ] <- paste0("(", res[s, ], ")")
}


xtable(res)
res<-readRDS(file.path(base_path,"aic", "criteria_alldata.RDS"))
#res<-res[,c(1,4,5,6,7,11,12,8,9)]
res<-res[c(1,2,3,4,5,7,6),]
res<-t(res)
#res
for (s in c(2)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(3,4)){
	res[s,]<-fd(res[s,],3)
}
#xtable(res)
tp(save=dir_path)
```


# model2
For the model 2, perform the same procedure.

```{r}
base_path <- here("out", "Sim2_01")
dir_path <- file.path(base_path, "aic")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 
```

Generate data
```{r,warning=FALSE}
set.seed(123)
n = 100
p = 200
q = 200
k = 5
simdata<-rdasim2(n = n,p = p,q = q,k = k,s2n=5)
X <- simdata$X
Y <- simdata$Y
```


```{r,eval=F}
set.seed(123)
rn_list <- list()

for (k in 1:100) {
  rn_list[[k]] <- sample(c(1:nrow(X)), 10, replace = FALSE)
}
saveRDS(rn_list,file.path(base_path, "rn_list.RDS"))
lm<-get_lambda_stars(dir_path, rn_list, Y=Y, X=X) 
```

```{r,eval=F}
set.seed(123)
#base_path <- here("out", "Sim2")
#res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))
lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))

Lambda<-rrr_lambda(Y = Y, X = X)
criteria_test_all(Y=Y,X=X,Lambda=Lambda,dir_path=dir_path,maxrank=10)

criteria_test(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)
#criteria_fit(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)
rsbc_test(Y=Y,X=X,save=dir_path)
tp(save=dir_path)
```

## table
```{r}
#base_path <- here("out", "Sim2")
res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

res<-res[c(1,2,3,4,5,7,6),c(1,4,5,6,7,11,12,8,9)]
res<-t(res)

for (s in c(2,3,5,6,7)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(9)) {
  res[s,]<-rd(res[s,],3)
}

for (s in c(4,7,8)){
	res[s,]<-fd(res[s,],3)
}


for (s in c(3,5,7,9)) {
  res[s, ] <- paste0("(", res[s, ], ")")
}

xtable(res)

res<-readRDS(file.path(base_path,"aic", "criteria_alldata.RDS"))
#res<-res[,c(1,4,5,6,7,11,12,8,9)]
res<-res[c(1,2,3,4,5,7,6),]
res<-t(res)
#res
for (s in c(2)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(3,4)){
	res[s,]<-fd(res[s,],3)
}

#xtable(res)
tp(save=dir_path)
```


# session info
check the info and environment
```{r}
devtools::session_info()
```
