
---
title: "Senario 2 : Computation Time on Simulation Data with RRDA"
output: html_document
author: "Hayato Yoshioka (University of Tokyo, AgroParisTech)"
---

# Overview. H.Yoshioka et al. (rrda package)

Senario 3 

Here, we perform comparison of computation time based on simulation data
Compare the rrpack vs rrda


ulimit -v 180000000 (180 GB. around 70% of memory)

# package
```{r}
library(furrr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(RSpectra)
library(rrpack)
library(rrda)
library(xtable)
library(here)
library(parallel)
```

Create the folder for saving
```{r}
dir_path<-here("out","benchmark")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 
```


various p are tested for the computataion time 

```{r}
measure_time <- function(fit_function, Y, X, timeout = 1) {
  tryCatch({
    # Run the computation in a separate process
    job <- mcparallel({
      system.time(fit_result <- fit_function(Y = Y, X = X, nrank = 5))
    })
    
    start_time <- Sys.time()
    
    # Check for results periodically
    repeat {
      result <- mccollect(job, wait = FALSE)
      
      # If result is available, return elapsed time
      if (!is.null(result)) {
        return(result[[1]][3])
      }
      
      # Check if timeout has been reached
      if (difftime(Sys.time(), start_time, units = "secs") > timeout) {
        cat("The process took more than", timeout, "seconds and was terminated.\n")
        
        # Terminate the child process
        tools::pskill(job$pid, signal = 9) # Force kill (UNIX-based systems)
        return(NA) # Indicate timeout
      }
      
      Sys.sleep(0.1)  # Small sleep to avoid busy-waiting
    }
  }, error = function(e) {
    # Handle errors gracefully by returning NA
    return(NA)
  })
}

```


# compute time
various p are tested for the computataion time 


```{r}
set.seed(123)

plist <- c(100,1000)
n_runs <- 10
mat <- matrix(NA, length(plist), 4)
colnames(mat) <- c("chen_mean", "chen_std", "hay_mean", "hay_std")
xylist <- list()

# Data generation and time measurement
for (num_p in seq_along(plist)) {
	p <- plist[num_p]
	print(p)
	
	chen_times <- numeric(n_runs)
	hay_times <- numeric(n_runs)
	
	for (i in 1:n_runs) {
		print(i)
		
		# Data generation
		mydata <- rdasim1(n = 100, p = p, q = p, k = 5)
		X <- mydata$X
		Y <- mydata$Y
		xylist[[num_p]] <- list(p = list(X = X, Y = Y))
		
		# Measure computation time for Chen (using the common function)
		chen_times[i] <- tryCatch({
  system.time(rfit <- rrs.fit(Y = Y, X = X, nrank = 5))[3]
    	}, error = function(e) {
    		NA
    		})

		# Measure computation time for Hay (using the common function
			
		options(future.globals.maxSize = 100 * 1024^3) 
		
	
		hay_times[i] <- tryCatch({
  	  system.time(rfit <- rrda.fit(Y = Y, X = X, nrank = 5))[3]
			
    	}, error = function(e) {
    		NA
    		})

		options(future.globals.maxSize = NULL) 
	}
	
	# Save mean and standard deviation to matrix
	mat[num_p, "chen_mean"] <- mean(chen_times)
	mat[num_p, "chen_std"] <- round(sd(chen_times) / sqrt(n_runs), 4)
	mat[num_p, "hay_mean"] <- mean(hay_times)
	mat[num_p, "hay_std"] <- round(sd(hay_times) / sqrt(n_runs), 4)
}

rownames(mat) <- plist

# Save results
saveRDS(mat, here(dir_path, "sim_time_1_6.RDS"))

#mat_1_6<-mat

```


# large


```{r}
set.seed(123)

plist <- c(10000,100000,1000000)
n_runs <- 1
mat <- matrix(NA, length(plist), 4)
colnames(mat) <- c("chen_mean", "chen_std", "hay_mean", "hay_std")
xylist <- list()

# Data generation and time measurement
for (num_p in seq_along(plist)) {
	p <- plist[num_p]
	print(p)
	
	chen_times <- numeric(n_runs)
	hay_times <- numeric(n_runs)
	
	for (i in 1:n_runs) {
		print(i)
		
		# Data generation
		mydata <- rdasim1(n = 100, p = p, q = p, k = 5)
		X <- mydata$X
		Y <- mydata$Y
		xylist[[num_p]] <- list(p = list(X = X, Y = Y))
		
		# Measure computation time for Chen (using the common function)
		
		#chen_times[i] <- measure_time(rrs.fit, Y, X)
		
		options(future.globals.maxSize = 100 * 1024^3) 
		
		# Measure computation time for Hay (using the common function)
		hay_times[i] <- measure_time(rrda.fit, Y, X)
		
		options(future.globals.maxSize = NULL) 
	}
	
	# Save mean and standard deviation to matrix
	mat[num_p, "chen_mean"] <- mean(chen_times)
	mat[num_p, "chen_std"] <- round(sd(chen_times) / sqrt(n_runs), 4)
	mat[num_p, "hay_mean"] <- mean(hay_times)
	mat[num_p, "hay_std"] <- round(sd(hay_times) / sqrt(n_runs), 4)
}

rownames(mat) <- plist

# Save results
saveRDS(mat, here(dir_path, "sim_time_5.RDS"))

#mat_5 <- mat

```


# Table
Show the result table
```{r}

format_without_leading_zero <- function(x) {
     s <- formatC(x, format="f", digits=2)
     return(s)
}

mat1_6 <- readRDS(here(dir_path,"sim_time_1_6.RDS"))
mat5 <- readRDS(here(dir_path,"sim_time_5.RDS"))

#mat<-rbind(mat1_6[c(1,2),],mat5,mat1_6[3,,drop=F])

mat <- rbind(mat1_6[c(1,2), , drop=FALSE], mat5, mat1_6[3, , drop=FALSE])


#mat<-mat[rownames(mat) %in% pl,]

formatted_mat <- apply(mat, 2, format_without_leading_zero)

table_latex <- xtable(formatted_mat)
table_latex

```

# session info
check the info and environment
```{r}
devtools::session_info()
```
