---
title: "Senario 3 : Random Splitting Process on Simulation Data with RRDA"
output: html_document
author: "Hayato Yoshioka (University of Tokyo, AgroParisTech)"
---

# Overview. H.Yoshioka et al. (rrda package)

Compare the rrda and stars, and other general criteria for parameter tuning and test to compute MSPE
For simulations (Model 1 and 2)
Also compare the several parameters (CV min, 1se Lambda, 1se rank, full rank, lambda 0, full + lambda 0)

# functions
```{r}
library(furrr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(RSpectra)
library(rrda)
library(here)
library(xtable)
library(pheatmap)
library(tictoc)
source("script_rrda/functions_rrda_yoshioka.R")
source("script_rrda/functions_stars_rrr_yoshioka.R")
```


# model1
create folders to save
```{r}
base_path <- here("out", "Sim1")
dir_path <- file.path(base_path, "aic")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 
```

Generate data
```{r,warning=FALSE}
set.seed(123)
n = 100
p = 200
q = 200
k = 5
simdata<-rdasim1(n = n,p = p,q = q,k = k)
X <- simdata$X
Y <- simdata$Y
```

Define samples to be extracted for Random Splitting process. (100 iterations)
Define the lambda range for each iteration. The lambda and sampling is set to be the same for every parameter tuning criteria.
```{r,eval=F}
set.seed(123)
rn_list <- list()

for (k in 1:100) {
  rn_list[[k]] <- sample(c(1:nrow(X)), 10, replace = FALSE)
}
saveRDS(rn_list,file.path(base_path, "rn_list.RDS"))
lm<-get_lambda_stars(dir_path, rn_list, Y=Y, X=X) 
```

Run the Random Splitting process and get the results
```{r,eval=F}
base_path <- here("out", "Sim1")
#res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

set.seed(123)

rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))
lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))

Lambda<-rrr_lambda(Y = Y, X = X)
criteria_test_all(Y=Y,X=X,Lambda=Lambda,dir_path=dir_path,maxrank=10)

criteria_test(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)

rsbc_test(Y=Y,X=X,save=dir_path)
tp(save=dir_path)
```


## table
Plot and Table of the results
```{r}
base_path <- here("out", "Sim1")
res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

res<-res[c(1,2,3,4,5,7,6),c(1,4,5,6,7,11,12,8,9)]
res<-t(res)
#res

for (s in c(2,3,5,6,7)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(9)) {
  res[s,]<-rd(res[s,],3)
}

for (s in c(4,7,8)){
	res[s,]<-fd(res[s,],3)
}


for (s in c(3,5,7,9)) {
  res[s, ] <- paste0("(", res[s, ], ")")
}


xtable(res)
res<-readRDS(file.path(base_path,"aic", "criteria_alldata.RDS"))
#res<-res[,c(1,4,5,6,7,11,12,8,9)]
res<-res[c(1,2,3,4,5,7,6),]
res<-t(res)
#res
for (s in c(2)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(3,4)){
	res[s,]<-fd(res[s,],3)
}
xtable(res)
tp(save=dir_path)
```



# model2
For the model 2, perform the same procedure.

```{r}
base_path <- here("out", "Sim2")
dir_path <- file.path(base_path, "aic")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 
```

Generate data
```{r,warning=FALSE}
set.seed(123)
n = 100
p = 200
q = 200
k = 5
simdata<-rdasim2(n = n,p = p,q = q,k = k,s2n=5)
X <- simdata$X
Y <- simdata$Y
```


```{r,eval=F}
set.seed(123)
rn_list <- list()

for (k in 1:100) {
  rn_list[[k]] <- sample(c(1:nrow(X)), 10, replace = FALSE)
}
saveRDS(rn_list,file.path(base_path, "rn_list.RDS"))
lm<-get_lambda_stars(dir_path, rn_list, Y=Y, X=X) 
```

```{r,eval=F}
set.seed(123)
base_path <- here("out", "Sim2")
#res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))
lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))

Lambda<-rrr_lambda(Y = Y, X = X)
criteria_test_all(Y=Y,X=X,Lambda=Lambda,dir_path=dir_path,maxrank=10)

criteria_test(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)
#criteria_fit(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)
rsbc_test(Y=Y,X=X,save=dir_path)
tp(save=dir_path)
```

## table
```{r}
base_path <- here("out", "Sim2")
res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

res<-res[c(1,2,3,4,5,7,6),c(1,4,5,6,7,11,12,8,9)]
res<-t(res)

for (s in c(2,3,5,6,7)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(9)) {
  res[s,]<-rd(res[s,],3)
}

for (s in c(4,7,8)){
	res[s,]<-fd(res[s,],3)
}


for (s in c(3,5,7,9)) {
  res[s, ] <- paste0("(", res[s, ], ")")
}

xtable(res)

res<-readRDS(file.path(base_path,"aic", "criteria_alldata.RDS"))
#res<-res[,c(1,4,5,6,7,11,12,8,9)]
res<-res[c(1,2,3,4,5,7,6),]
res<-t(res)
#res
for (s in c(2)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(3,4)){
	res[s,]<-fd(res[s,],3)
}

xtable(res)
tp(save=dir_path)
```


# session info
check the info and environment
```{r}
devtools::session_info()
```

