
---
title: "Senario 2 : Rank Estimate Evaluation on Simulation Data with RRDA"
output: html_document
author: "Hayato Yoshioka (University of Tokyo, AgroParisTech)"
---

# Overview. H.Yoshioka et al. (rrda package)

Senario 2 

Here, we perform rank evaluation for simulation data sets.
We test various n,p,q,k parameters for the data generation

We evaluate the model by checking the percentage of the right rank estimation and the correlation between true and estimated rank.


# package
```{r}
library(furrr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(RSpectra)
library(rrda)
library(xtable)
library(purrr) 
library(here)
library(progress)
source("script_rrda/functions_rrda_yoshioka.R")
```

Create the folder for saving
```{r}
dir_path<- here("out/eval")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 
```


# simulation run 
2 types of simulations and 3 types of matrix size are tested
```{r,eval=F}
set.seed(123)

n_iterations=100
# Define your conditions
simulations <- c("sim1", "sim2")
sizes <- c("large", "small", "mixed")

# Loop over each combination
for (sim in simulations) {

  for (size in sizes) {
    # Run your function with each combination
    data_list <- rank_evaluate(n_iterations = n_iterations, rdasim = sim, size = size)
    # Save the results
    filename <- paste0("data_list_", sim, "_", size, ".rds")
    saveRDS(data_list, file = here("out/eval", filename))
    data_list<-readRDS(here("out/eval", filename))
    plot_evaluate(data_list,rdasim = sim,size=size)
  }
}

```

# get result
Plot the results
```{r}
set.seed(123)
n_iterations=100
# Define your conditions
 simulations <- c("sim1", "sim2")
 sizes <- c("large", "small", "mixed")

for (sim in simulations) {

  for (size in sizes) {
  	filename <- paste0("data_list_", sim, "_", size, ".rds")
		data_list<-readRDS(here("out/eval", filename))
    plot_evaluate(data_list,rdasim = sim,size=size)
    
  }
}
```

# session info
check the info and environment
```{r}
devtools::session_info()
```
