
---
title: 'Senario 0 (visualization) : Cross Validation and Fitting on Simulation Data with RRDA'
output:
  html_document: default
author: "Hayato Yoshioka (University of Tokyo, AgroParisTech)"
---

# Overview. H.Yoshioka et al. (rrda package)

Senario 1

Here, we perform the parameter tuning for lambda and rank and fitting. After obtaining the parameters, the model is also tested.

Data generation is based on two types of methods, called simulation 1 (Latent Space Model) and simulation 2 (Matrix Factorization Model).


```{r}
library(furrr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(RSpectra)
library(rrda)
library(xtable)
library(here)
```

# simulation 1 (Latent Space Model)

Create folder for saving
```{r}
base_path <- here("out", "senario0")
dir_path <- file.path(base_path, "sim1")
if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 
```


## whole data
In this section, whole data is used for parameter tuning (cv) and test

Generate data
```{r,warning=FALSE}
set.seed(123)
n = 100
p = 200
q = 200
k = 5
simdata<-rdasim1(n = n,p = p,q = q,k = k,s2n = c(1, 1))
X <- simdata$X
Y <- simdata$Y
```

rrda.cv on whole data
```{r,eval=F}
plan(multisession)
cv_result<- rrda.cv(Y = Y, X = X,lambda = NULL,maxrank = 10,nfold=5, scale.X = F,scale.Y = F)
plan(sequential)

saveRDS(cv_result,file.path(dir_path, "whole_cv.RDS"))
```

Plot the results
```{r,warning=FALSE}
cv_result <- readRDS(file.path(dir_path, "whole_cv.RDS"))
rrda.plot(cv_result = cv_result)
rrda.plot(cv_result = cv_result,show_error_bar = T)
rrda.heatmap(cv_result)
rrda.summary(cv_result)

# get mse and sem for each rank
m <- apply(cv_result$MSE, 1, min)
min_indices <- apply(cv_result$MSE, 1, which.min)
std <- cv_result$SEM[cbind(1:nrow(cv_result$SEM), min_indices)]
result1 <- cbind(m, std)

```

Plot the result
```{r,fig.width=6,fig.height=6}
b<-rrda.fit(Y,X,nrank = cv_result$opt_min$rank, lambda = cv_result$opt_min$lambda,scale.X = F,scale.Y = F)

pred<-rrda.predict(Bhat=b,X = X)[[1]][[1]][[1]]

min<- min(Y)
max<- max(Y)
plot(Y,pred,cex = 0.1,xlim =c(min,max),ylim = c(min,max),ylab = "Prediction",cex.lab=1.3)
abline(0,1,col=2)

codna<-diag(cor(Y,pred))
mean(codna)

hist(codna,main="Fitting COR for predicted variales")

```

## train test
sampled data is used for parameter tuning (cv) and rest of the data is used for test

data is splitted to train data (n=90) and test data (n=10)
```{r}
set.seed(123)

rn<-c(1:10)
X_train<-X[-rn,]
Y_train<-Y[-rn,]
X_test<-X[rn,]
Y_test<-Y[rn,]
```

rrda.cv on training data
```{r,eval=F}
plan(multisession)
cv_result<- rrda.cv(Y = Y_train, X = X_train,lambda = NULL,maxrank = 10,scale.X = F,scale.Y = F)
plan(sequential)
saveRDS(cv_result,file.path(dir_path, "tt_cv.RDS"))
```

Plot the result
```{r}
cv_result <- readRDS(file.path(dir_path, "tt_cv.RDS"))
rrda.plot(cv_result = cv_result)
rrda.plot(cv_result = cv_result,show_error_bar = T)
rrda.heatmap(cv_result)
rrda.summary(cv_result)
```

Check fitting
```{r,fig.width=6,fig.height=6}
b<-rrda.fit(Y = Y_train, X = X_train,nrank = cv_result$opt_min$rank, lambda = cv_result$opt_min$lambda,scale.X = F,scale.Y = F)

pred<-rrda.predict(Bhat=b,X = X_test)[[1]][[1]][[1]]

min<- min(Y)
max<- max(Y)
plot(Y_test,pred,cex = 0.5,xlim =c(min,max),ylim = c(min,max),ylab = "Prediction",cex.lab=1.3)
abline(0,1,col=2)

codna<-diag(cor(Y_test,pred))
mean(codna)

hist(codna,main="Fitting COR for predicted variales")

```

# simulation 2 (Matrix Factorization Model)
Here we perform the same procdure for model 2

```{r}
base_path <- here("out", "senario0")
dir_path <- file.path(base_path, "sim2")
if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 
```

## whole data
all data is used for parameter tuning (cv) and test

data
```{r,warning=FALSE}
set.seed(123)
n = 100
p = 200
q = 200
k = 5

simdata<-rdasim2(n = n,p = p,q = q,k = k,s2n=1)
X <- simdata$X
Y <- simdata$Y

B <- simdata$B
E <- simdata$E
```

cv
```{r,eval=F}
plan(multisession)
cv_result<- rrda.cv(Y = Y, X = X,lambda = NULL,maxrank = 10,nfold=5,scale.X = F,scale.Y = F)
plan(sequential)
saveRDS(cv_result,file.path(dir_path, "whole_cv.RDS"))
```

Plot the results
```{r,warning=FALSE}
cv_result <- readRDS(file.path(dir_path, "whole_cv.RDS"))
rrda.plot(cv_result = cv_result)
rrda.plot(cv_result = cv_result,show_error_bar = T)
rrda.heatmap(cv_result)
rrda.summary(cv_result)

# get mse and sem for each rank
m <- apply(cv_result$MSE, 1, min)
min_indices <- apply(cv_result$MSE, 1, which.min)
std <- cv_result$SEM[cbind(1:nrow(cv_result$SEM), min_indices)]
result2 <- cbind(m, std)

```

fit
```{r,fig.width=6,fig.height=6}
b<-rrda.fit(Y,X,nrank = cv_result$opt_min$rank, lambda = cv_result$opt_min$lambda,scale.X = F,scale.Y = F)

pred<-rrda.predict(Bhat=b,X = X)[[1]][[1]][[1]]

min<- min(Y)
max<- max(Y)
plot(Y,pred,cex = 0.1,xlim =c(min,max),ylim = c(min,max),ylab = "Prediction",cex.lab=1.3)
abline(0,1,col=2)

plot(Y,X %*% B,cex = 0.1,xlim =c(min,max),ylim = c(min,max),ylab = "XB",cex.lab=1.3)
abline(0,1,col=2)

codna<-diag(cor(Y,pred))
mean(codna)

hist(codna,main="Fitting COR for predicted variales")

```


## train test

sampled data is used for parameter tuning (cv) and rest of the data is used for test
data is splitted to train data (n=90) and test data (n=10)

```{r}
set.seed(123)

rn<-c(1:10)
X_train<-X[-rn,]
Y_train<-Y[-rn,]
X_test<-X[rn,]
Y_test<-Y[rn,]
```

cv
```{r,eval=F}
plan(multisession)
cv_result<- rrda.cv(Y = Y_train, X = X_train,lambda = NULL,maxrank = 10,scale.X = F,scale.Y = F)
plan(sequential)
saveRDS(cv_result,file.path(dir_path, "tt_cv.RDS"))
```

Plot the resuts
```{r}
cv_result <- readRDS(file.path(dir_path, "tt_cv.RDS"))
rrda.plot(cv_result = cv_result)
rrda.plot(cv_result = cv_result,show_error_bar = T)
rrda.heatmap(cv_result)
rrda.summary(cv_result)
```

fit
```{r,fig.width=6,fig.height=6}
b<-rrda.fit(Y = Y_train, X = X_train,nrank = cv_result$opt_min$rank, lambda = cv_result$opt_min$lambda,scale.X = F,scale.Y = F)

pred<-rrda.predict(Bhat=b,X = X_test)[[1]][[1]][[1]]

min<- min(Y)
max<- max(Y)
plot(Y_test,pred,cex = 0.5,xlim =c(min,max),ylim = c(min,max),ylab = "Prediction",cex.lab=1.3)
abline(0,1,col=2)

plot(Y_test,X_test %*% B,cex = 0.5,xlim =c(min,max),ylim = c(min,max),ylab = "X_test B",cex.lab=1.3)
abline(0,1,col=2)

codna<-diag(cor(Y_test,pred))
mean(codna)

hist(codna,main="Fitting COR for predicted variales")

```

# table for the results
THe table for simulation 1 and 2 (Whole data)
```{r}
lat<-cbind(result1,result2)

format_without_leading_zero <- function(x) {
     s <- formatC(x, format="f", digits=4)  
     return(s)
}

lat <- apply(lat, 2, format_without_leading_zero)

xtable(lat)
```

# session info
check the info and environment
```{r}
devtools::session_info()
```
