---
title: "rrda: Ridge Redundancy Analysis for High-Dimensional Omics Data"
author: "Hayato Yoshioka (University of Tokyo)"
date: "2025-10-02"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
      position: left
    number_sections: 1
---

# Summary of R package **rrda** Workshop

This page is designed for a workshop on the R package **rrda** (Ridge Redundancy Analysis for High-Dimensional Omics Data), available on [CRAN](https://CRAN.R-project.org/package=rrda).  

The **rrda** package is designed for analyzing **two matrices**, exploring how one may **influence or explain** the other.

While conventional methods of RDA (or RRDA) are restricted to relatively small matrices, **rrda** extends these computations to **high-dimensional data**—including datasets with more than **100,000 features**.  

This capability makes it especially valuable in modern **omics sciences** and other fields where analyzing extremely large datasets is essential.



---

# Algebra

## Classic formula 
The Ridge Redundancy Analysis model is represented as:

Let \( Y \) be an \( n \times q \) matrix of response variables, and let \( X \) be an \( n \times p \) matrix of predictor variables. We assume that the columns of matrices \( Y \) and \( X \) are centered to have means of 0.

The relation between \(X\) and \(Y\) is given by

$$
Y = X B + E
$$

where \( B \) is the matrix of regression coefficients, and \( E \) is an error matrix.  

The ridge RDA aims to estimate \( B \) under both rank and ridge restrictions. The corresponding optimization problem is

$$
\hat{B}(\lambda, r) = \arg\min_B \left\{ \| Y - X B \|^2 + \lambda \| B \|^2 \right\}
\quad \text{subject to} \quad \text{rank}(B) \leq r
$$

where \(\| A \|^2 = \text{tr}(A'A)\) is the Frobenius norm and \(\lambda\) is the ridge regularization parameter.

---

##  For High-Dimensional Data 

For Ridge Redundancy Analysis, the ridge estimator \(\hat{B}(\lambda)\) can be decomposed as follows:

$$
U_{\hat{B}(\lambda)} = V (D^{2} + \lambda I)^{-1/2}\hat{U}_{\lambda}, \quad
D_{\hat{B}(\lambda)} = \hat{D}_{\lambda}, \quad
V_{\hat{B}(\lambda)} = \hat{V}_{\lambda}
$$

where the Singular Value Decomposition (SVD) of \( X \) is 
$$
X = U D V^{\prime}
$$
and \(\hat{U}_{\lambda}, \hat{D}_{\lambda}, \hat{V}_{\lambda}\) are the SVD components of

$$
M_\lambda = (D^{2} + \lambda I)^{-1/2} D U^{\prime} Y.
$$

Since \(M_\lambda\) depends on \(\lambda\), its SVD must be computed for **each** value of \(\lambda\).  
However, efficiency can be gained because \(M_\lambda\) is the product of:

- a diagonal matrix \((D^{2} + \lambda I)^{-1/2}\), and  
- a constant matrix \(U'Y\) (independent of \(\lambda\)).

---

## Final Expression 

The rank-restricted ridge estimator is:

$$
\hat{B}(\lambda,r) =
V(D^{2} + \lambda I)^{-1/2}
\hat{U}_{\lambda}^{[r]}
\hat{D}_{\lambda}^{[r]}
\hat{V}_{\lambda}^{[r]\prime}.
$$



**Important Note 1:** Ridge Redundancy Analysis (RRDA) has **two parameters**:  
- **Ridge penalty \(\lambda\) **
- **Rank \(r\)**


**Important Note 2:** RRDA is efficiently rewritten with **SVD of X**


---

# Setup

Required packages
```{r}
pkgs <- c("rrda", "stringr")

# Install missing packages
to_install <- pkgs[!(pkgs %in% installed.packages()[, "Package"])]
if (length(to_install)) {
  install.packages(to_install, repos = "https://cloud.r-project.org")
}


op <- old.packages(repos = "https://cloud.r-project.org")
if (!is.null(op) && "rrda" %in% rownames(op)) {
  install.packages("rrda", repos = "https://cloud.r-project.org")
}


# load packages
library(rrda)
library(stringr)

```


# Simulation

## Data generation  

Here we generate two matrices, **X** and **Y**, with a chosen rank constraint **k**.

```{r}
set.seed(10)
simdata<-rdasim1(n = 50,p = 100,q = 100,k = 5)
X <- simdata$X
Y <- simdata$Y

```

## Parameter tuning 
```{r}
cv_result<- rrda.cv(Y = Y, X = X,nfold = 5)
rrda.summary(cv_result = cv_result)
```

## Visualize Results 

Here we illustrate the parameter tuning process (regularization path), which helps identify the optimal parameter for maximizing prediction accuracy from **X** to **Y**.

```{r}
p <- rrda.plot(cv_result) # cv result plot
print(p)
h <- rrda.heatmap(cv_result) # cv result heatmap
print(h)

best_lambda<-cv_result$opt_min$lambda  # selected parameter
best_rank<-cv_result$opt_min$rank # selected parameter

Bhat <- rrda.fit(Y = Y, X = X, nrank = best_rank,lambda = best_lambda) # fitting
Bhat_mat<-rrda.coef(Bhat)
Yhat_mat <- rrda.predict(Bhat = Bhat, X = X) # prediction
Yhat<-Yhat_mat[[1]][[1]][[1]] # predicted values

cor_Y_Yhat<-diag(cor(Y,Yhat)) # correlation
summary(cor_Y_Yhat)

plot(Yhat, Y)
abline(0, 1, col = "red") 
```


## Two-Dimensional Plot 

Traditionally, (Ridge) RDA is visualized in **two dimensions**.  
However, in omics studies, this approach can sometimes **overload the plot** with information, making interpretation challenging.


```{r}
# You want to specify one lambda in `rrda.fit` to visualize

ud<-Bhat$Bhat_comp[[1]][[1]] # SVD component of B (UD)
v <-Bhat$Bhat_comp[[1]][[2]] # SVD component of B (V)

ud12 <- ud[, 1:2]
v12 <- v[, 1:2]

# Base plot: ud (e.g., site scores)
plot(v12, 
     xlab = "RRDA1", ylab = "RRDA2", 
     xlim = range(c(ud12[,1], v12[,1])) * 1.1, 
     ylim = range(c(ud12[,2], v12[,2])) * 1.1, 
     pch = 19, col = "darkgreen", 
     main = "RRDA")

# Add v (e.g., species scores) as arrows from origin
arrows(0, 0, ud12[,1], ud12[,2], col = "blue3", length = 0.1)

# Optionally add text labels
text(ud12, labels = paste0("X", 1:nrow(ud12)), pos = 3, col = "blue3", cex = 0.6)
text(v12, labels = paste0("Y", 1:nrow(v12)), pos = 3, col = "darkgreen", cex = 0.6)
```

## Top Feature Heatmap 

For better interpretability, we visualize the **feature–feature matrix** using a selected dimensionality, highlighting the most informative features.

```{r,fig.height=5,fig.width=5}
best_lambda<-cv_result$opt_min$lambda  
best_rank<-cv_result$opt_min$rank
rrda.top(Y=Y,X=X,nrank=best_rank,lambda=best_lambda,mx=20,my=20)
```

# Application

As an application, we analyze **microbiome** and **metabolome** data from soybean grown under drought conditions.  
The dataset comes from a 2019 field experiment at Tottori University (Yoshioka et al. 2025).

## Read data 

Data is available on GitHub (`https://github.com/Yoska393/rrda/blob/main/RDAdata/SoyData.RDS`).
```{r}
#download from github
if(!dir.exists("RDAdata")) dir.create("RDAdata")
url <- "https://raw.githubusercontent.com/Yoska393/rrda/main/RDAdata/SoyData.RDS"
destfile <- "RDAdata/SoyData.RDS"

if (!file.exists(destfile)) {
  download.file(url, destfile, mode = "wb")
  message("✅ File downloaded successfully.")
} 

SoyData <- readRDS("RDAdata/Soydata.RDS")

met <- SoyData$metabolome
micro <- SoyData$microbiome

metname<-substr(SoyData$metname, 1, 30)
microname<-str_extract(SoyData$microname, "(?<=o__)[^;]+(?=; f__)")

Y <- met
X <- micro

colnames(Y)<-metname
colnames(X)<-microname

dim(Y)
dim(X)
```

## Parameter tuning 
```{r}
cv_result<- rrda.cv(Y = Y, X = X, nfold = 5)
rrda.summary(cv_result = cv_result)
```
 
## Visualize Results 
```{r}
p <- rrda.plot(cv_result) # cv result plot
print(p)
h <- rrda.heatmap(cv_result) # cv result heatmap
print(h)

best_lambda<-cv_result$opt_min$lambda  # selected parameter
best_rank<-cv_result$opt_min$rank # selected parameter

Bhat <- rrda.fit(Y = Y, X = X, nrank = best_rank,lambda = best_lambda)
```


## Fitting 
```{r}
# fitting
Bhat_mat<-rrda.coef(Bhat)
Yhat_mat <- rrda.predict(Bhat = Bhat, X = X) # prediction
Yhat<-Yhat_mat[[1]][[1]][[1]] # predicted values

cor_Y_Yhat<-diag(cor(Y,Yhat)) # correlation
summary(cor_Y_Yhat)

plot(Yhat, Y)
abline(0, 1, col = "red") 
```

## Top Feature Heatmap 

In the lower-dimensional space, we observe several **interesting interactions** among the top features.

```{r,fig.height=7,fig.width=7}
best_lambda<-cv_result$opt_min$lambda  # selected parameter
best_rank<-cv_result$opt_min$rank # selected parameter
rrda.top(Y=Y,X=X,nrank=best_rank,lambda=best_lambda,mx=20,my=20)
```


 
# References {-}
Yoshioka H, Aubert J, and Mary-Huard T (2025). rrda: Ridge Redundancy Analysis for High-Dimensional Omics Data.  https://CRAN.R-project.org/package=rrda (CRAN R Package) 

Yoshioka, H., Aubert, J., Iwata, H., and Mary-Huard, T., 2025. Ridge Redundancy Analysis for High-Dimensional Omics Data. bioRxiv, https://doi.org/10.1101/2025.04.16.649138



