---
title: "Ridge Redundancy Analysis for High-Dimensional Omics Data"
author: "Hayato Yoshioka"
date: "2025-10-02"
output: html_document
---

# R package **rrda** Workshop

This page is designed for a workshop on the R package **rrda** (Ridge Redundancy Analysis for High-Dimensional Omics Data), available on [CRAN](https://CRAN.R-project.org/package=rrda).  

The **rrda** package is designed for analyzing **two matrices**, exploring how one may **influence or explain** the other.

While conventional methods of RDA (or RRDA) are restricted to relatively small matrices, **rrda** extends these computations to **high-dimensional data**—including datasets with more than **100,000 features**.  

This capability makes it especially valuable in modern **omics sciences** and other fields where analyzing extremely large datasets is essential.

# Setup

Required package
```{r}
library(rrda)
library(pheatmap)
library(stringr)
library(grid)
```

function for top feature representation
```{r}

rrda.top<-function(cv_result,Y,X,mx=20,my=20,rank=NULL,lambda=NULL,title=NULL){
	
	
  if (mx > ncol(X)) {
    warning("mx is larger than ncol(X). Setting mx = ncol(X).")
    mx <- ncol(X)
  }
  if (my > ncol(Y)) {
    warning("my is larger than ncol(Y). Setting my = ncol(Y).")
    my <- ncol(Y)
  }
	
	K <- rank
	L <- lambda
  
	#Extract optimal lambda and rank
	if (is.null(K)) {
	K <- cv_result$opt_min$rank
	message(paste("K is set as the best rank", K, "selected by CV"))
	}
	
	if (is.null(L)) {
	  L <- cv_result$opt_min$lambda
	  message(paste("L is set as the best lambda", L, "selected by CV"))
	}

	# Fit the model using the optimal lambda and rank
	b <- rrda.fit(Y = Y, X = X, lambda = L, nrank = K)
	
	b1<-b$Bhat_comp[[1]][[1]]
	b2<-b$Bhat_comp[[1]][[2]]
	
	rownames(b1)<-colnames(X)
	rownames(b2)<-colnames(Y)
	
	x_scores <- apply(b1, 1, function(row) sqrt(sum(row^2)))
	top_x_idx <- order(x_scores, decreasing = TRUE)[1:mx]  # so that it becomes 30 variables afetr filtering
	
	y_scores <- apply(b2, 1, function(row) sqrt(sum(row^2)))
	top_y_idx <- order(y_scores, decreasing = TRUE)[1:my] # so that it becomes 30 variables afetr filtering
	
	b1_sub <- b1[top_x_idx, , drop = FALSE]  
	b2_sub <- b2[top_y_idx, , drop = FALSE]  
	
	B_sub <- b1_sub %*% t(b2_sub)
	
	h<-B_sub 
	max_value <- max(h, na.rm = TRUE)
	min_value <- min(h, na.rm = TRUE)
	
	custom_colors <- colorRampPalette(c("blue", "white", "red"))(200)
	max_abs_value <- max(abs(c(min_value, max_value)))
	breaks <- seq(-max_abs_value, max_abs_value, length.out = 201)
	
	main_title <- NULL
  if (isFALSE(title)) {
    main_title <- NULL
  } else if (is.null(title)) {
    main_title <- sprintf("RRDA (rank = %s, lambda = %s)", K, L)
  } else if (is.character(title) && length(title) == 1) {
    main_title <- title
  } else {
    warning("`title` must be a single string, NULL, or FALSE. Falling back to default.")
    main_title <- sprintf("Ridge RDA (rank = %s, lambda = %s)", K, L)
  }
	
	
	hp<-pheatmap(h,
					 color = custom_colors,
					 breaks = breaks,
					 border_color = NA,
					 #scale = "row",
					 clustering_distance_rows = "euclidean",
					 clustering_distance_cols = "euclidean",
					 clustering_method = "complete",
					 show_rownames = TRUE,
					 show_colnames = TRUE,
					 fontsize_row = 8,
					 fontsize_col =8,
					 width = 10,
					 height = 15,
					 main = main_title
	) 
	#grid.text(title, x = 0.5, y = 0.98,
   #       gp = gpar(fontsize = 14, fontface = "bold"))
	
	
	print(hp)
	
	
}

```


# Simulation

## Data generation 

Here we generate two matrices, **X** and **Y**, with a chosen rank constraint **k**.

```{r}
set.seed(10)
simdata<-rdasim1(n = 50,p = 100,q = 100,k = 5)
X <- simdata$X
Y <- simdata$Y

colnames(X) <- paste0("X", 1:ncol(X))
colnames(Y) <- paste0("Y", 1:ncol(Y))
```

## Cross validation for parameter tuning
```{r}
cv_result<- rrda.cv(Y = Y, X = X,nfold = 5)
rrda.summary(cv_result = cv_result)
```

## Visualize and Select the Best Parameter

Here we illustrate the parameter tuning process (regularization path), which helps identify the optimal parameter for maximizing prediction accuracy from **X** to **Y**.

```{r}
p <- rrda.plot(cv_result) # cv result plot
print(p)
h <- rrda.heatmap(cv_result) # cv result heatmao
print(h)

estimated_lambda<-cv_result$opt_min$lambda  # selected parameter
estimated_rank<-cv_result$opt_min$rank # selected parameter

Bhat <- rrda.fit(Y = Y, X = X, nrank = estimated_rank,lambda = estimated_lambda) # fitting
Bhat_mat<-rrda.coef(Bhat)
Yhat_mat <- rrda.predict(Bhat = Bhat, X = X) # prediction
Yhat<-Yhat_mat[[1]][[1]][[1]] # predicted values

cor_Y_Yhat<-diag(cor(Y,Yhat)) # correlation
summary(cor_Y_Yhat)

plot(Yhat, Y)
abline(0, 1, col = "red") 
```


## Two-Dimensional Plot

Traditionally, (Ridge) RDA is visualized in **two dimensions**.  
However, in omics studies, this approach can sometimes represent **too much information at once**, making interpretation challenging.


```{r}
# You want to specify one lambda in `rrda.fit` to visualize

ud<-Bhat$Bhat_comp[[1]][[1]] # SVD component of B (UD)
v <-Bhat$Bhat_comp[[1]][[2]] # SVD component of B (V)

ud12 <- ud[, 1:2]
v12 <- v[, 1:2]

# Base plot: ud (e.g., site scores)
plot(v12, 
     xlab = "RRDA1", ylab = "RRDA2", 
     xlim = range(c(ud12[,1], v12[,1])) * 1.1, 
     ylim = range(c(ud12[,2], v12[,2])) * 1.1, 
     pch = 19, col = "darkgreen", 
     main = "RDA")

# Add v (e.g., species scores) as arrows from origin
arrows(0, 0, ud12[,1], ud12[,2], col = "blue3", length = 0.1)

# Optionally add text labels
text(ud12, labels = paste0("X", 1:nrow(ud12)), pos = 3, col = "blue3", cex = 0.6)
text(v12, labels = paste0("Y", 1:nrow(v12)), pos = 3, col = "darkgreen", cex = 0.6)
```

## Top Feature Heatmap

For better interpretability, we visualize the **feature–feature matrix** using a selected dimensionality, highlighting the most informative features.

```{r}
rrda.top(cv_result=cv_result,Y=Y,X=X,mx=20,my=20)
```

# Application

As an application, we analyze **microbiome** and **metabolome** data from soybean grown under drought conditions.  
The dataset comes from a 2019 field experiment at Tottori University (Yoshioka et al. 2025).

## Read data

Data is available on [GitHub](https://raw.githubusercontent.com/Yoska393/rrda/main/RDAdata/SoyData.RDS). 
```{r}
SoyData <- readRDS("RDAdata/Soydata.RDS")
met <- SoyData$metabolome
micro <- SoyData$microbiome

metname<-substr(SoyData$metname, 1, 30)
microname<-str_extract(SoyData$microname, "(?<=o__)[^;]+(?=; f__)")

Y <- met
X <- micro

colnames(Y)<-metname
colnames(X)<-microname

dim(Y)
dim(X)
```

## Cross validation for parameter tuning
```{r}
cv_result<- rrda.cv(Y = Y, X = X, nfold = 5)
rrda.summary(cv_result = cv_result)
```

## Visusalize and extract best parameter
```{r}
p <- rrda.plot(cv_result) # cv result plot
print(p)
h <- rrda.heatmap(cv_result) # cv result heatmao
print(h)

estimated_lambda<-cv_result$opt_min$lambda  # selected parameter
estimated_rank<-cv_result$opt_min$rank # selected parameter

Bhat <- rrda.fit(Y = Y, X = X, nrank = estimated_rank,lambda = estimated_lambda)
```


## Fittitng
```{r}
# fitting
Bhat_mat<-rrda.coef(Bhat)
Yhat_mat <- rrda.predict(Bhat = Bhat, X = X) # prediction
Yhat<-Yhat_mat[[1]][[1]][[1]] # predicted values

cor_Y_Yhat<-diag(cor(Y,Yhat)) # correlation
summary(cor_Y_Yhat)

plot(Yhat, Y)
abline(0, 1, col = "red") 
```

## Top Feature Heatmap

In the lower-dimensional space, we observe several **interesting interactions** among the top features.

```{r,fig.height=7,fig.width=7}
rrda.top(cv_result=cv_result,Y=Y,X=X,mx=20,my=20)
```



# References
Yoshioka H, Aubert J, and Mary-Huard T (2025). rrda: Ridge Redundancy Analysis for High-Dimensional Omics Data.  https://CRAN.R-project.org/package=rrda (CRAN R Package) 

Yoshioka, H., Aubert, J., Iwata, H., and Mary-Huard, T., 2025. Ridge Redundancy Analysis for High-Dimensional Omics Data. bioRxiv, https://doi.org/10.1101/2025.04.16.649138



