
---
title: "Application : Random Splitting on Application Data"
output: html_document
author: "Hayato Yoshioka (University of Tokyo, AgroParisTech)"
---

# Overview. H.Yoshioka et al. (rrda package)

Compare the rrda and stars, and other general criteria for parameter tuning and test to compute MSPE
For applications (Breast Cancer (ch13, ch all), Soybean, Methylation)


# functions
```{r}
library(furrr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(RSpectra)
library(rrda)
library(here)
library(xtable)
library(pheatmap)
library(tictoc)
source("script_rrda/functions_rrda_yoshioka.R")
source("script_rrda/functions_stars_rrr_yoshioka.R")
```


# chrom 13 only
```{r,eval=T}
da<-readRDS(here("RDAdata","breast.RDS"))
base_path <- here("out", "BreastCancer")
dir_path <- file.path(base_path, "aic_ch13")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 

dna<-t(da$dna)
rna<-t(da$rna)
dch<-da$chrom
rch<-da$genechr
rch[is.na(rch)]<-0

Y<-dna[,dch==13]
X<-rna[,rch==13]
```

make rabdom sampling rule
make lambda accoring to rrr (and stars)

```{R,eval=F}
set.seed(123)

rn_list <- list()

for (k in 1:100) {
  rn_list[[k]] <- sample(c(1:nrow(Y)), 10, replace = FALSE)
}
saveRDS(rn_list,file.path(base_path, "rn_list.RDS"))
lm<-get_lambda_stars(dir_path, rn_list, Y=Y, X=X) 

```


criteria comparison (stars included)
```{r,eval=F}
set.seed(123)

lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))
rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))

Lambda<-rrr_lambda(Y = Y, X = X)
criteria_test_all(Y=Y,X=X,Lambda=Lambda,dir_path=dir_path,maxrank=10)

criteria_test(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)
#criteria_fit(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=15)
rsbc_test(Y=Y,X=X,save=dir_path)
tp(save=dir_path)
```

results
```{r}
base_path <- here("out", "BreastCancer")
dir_path <- file.path(base_path, "aic_ch13")
res<-readRDS(file.path(base_path,"aic_ch13", "criteria.RDS"))

res<-res[c(1,2,3,4,5,7,6),c(1,4,5,6,7,11,12,8,9)]
res<-t(res)
res
for (s in c(2,3,6,7)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(4,5,8,9)){
	res[s,]<-fd(res[s,],3)
}

for (s in c(3,5,7,9)) {
  res[s, ] <- paste0("(", res[s, ], ")")
}

xtable(res)

res<-readRDS(file.path(base_path,"aic_ch13", "criteria_alldata.RDS"))
res<-res[c(1,2,3,4,5,7,6),]
res<-t(res)

for (s in c(2)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(3,4)){
	res[s,]<-fd(res[s,],3)
}

xtable(res)
tp(save=dir_path)

```

#ch all

```{R}
da<-readRDS(here("RDAdata","breast.RDS"))
base_path <- here("out", "BreastCancer")
dir_path <- file.path(base_path, "aic_all")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 

dna<-t(da$dna)
rna<-t(da$rna)
dch<-da$chrom
rch<-da$genechr
rch[is.na(rch)]<-0

Y<-dna
X<-rna
```

make rabdom sampling rule
make lambda accoring to rrr (and stars)
```{R,eval=F}
set.seed(123)

rn_list <- list()

for (k in 1:100) {
  rn_list[[k]] <- sample(c(1:nrow(Y)), 10, replace = FALSE)
}
saveRDS(rn_list,file.path(base_path, "rn_list.RDS"))
lm<-get_lambda_stars(dir_path, rn_list, Y=Y, X=X) 
```

all and rs
```{r,eval=F}
set.seed(123)

rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))
lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))

Lambda<-rrr_lambda(Y = Y, X = X)
criteria_test_all(Y=Y,X=X,Lambda=Lambda,dir_path=dir_path,maxrank=40)

#criteria_test(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=63,criteria= c("AIC", "BIC", "GIC", "BICP", "GCV","rrda"))
criteria_test(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=63)
#criteria_fit(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=63)
rsbc_test(Y=Y,X=X,save=dir_path)
tp(save=dir_path)
```

all and rs stars
```{r}
set.seed(123)

rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))
lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))
dir_path <- file.path(base_path, "aic_all/stars")

criteria_test(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=63,criteria= c("StARS"))

```

table
```{r}
base_path <- here("out", "BreastCancer")
dir_path <- file.path(base_path, "aic_all")

res<-readRDS(file.path(base_path,"aic_all", "criteria.RDS"))
res<-res[c(1,2,3,4,5,7,6),c(1,4,5,6,7,11,12,8,9)]
res<-t(res)
for (s in c(2,3,6,7)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(4,5,8,9)){
	res[s,]<-fd(res[s,],3)
}
for (s in c(3,5,7,9)) {
  res[s, ] <- paste0("(", res[s, ], ")")
}


xtable(res)

res<-readRDS(file.path(base_path,"aic_all", "criteria_alldata.RDS"))
#res<-res[,c(1,4,5,6,7,11,12,8,9)]
res<-res[c(1,2,3,4,5,7,6),]
res<-t(res)

for (s in c(2)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(3,4)){
	res[s,]<-fd(res[s,],3)
}


#res
xtable(res)


tp(save=dir_path)

```


# soybean

```{r}
base_path <- here("out", "Soy")
dir_path <- file.path(base_path, "aic")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 

SoyData<-readRDS(here("RDAdata","Soydata.RDS"))
met <- SoyData$metabolome
micro <- SoyData$microbiome

Y <- met
X <- micro
```


```{r}
set.seed(123)
rn_list <- list()

for (k in 1:100) {
  rn_list[[k]] <- sample(c(1:nrow(X)), 20, replace = FALSE)
}
saveRDS(rn_list,file.path(base_path, "rn_list.RDS"))
lm<-get_lambda_stars(dir_path, rn_list, Y=Y, X=X) 
```

```{r}
set.seed(123)

rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))
lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))

Lambda<-rrr_lambda(Y = Y, X = X)
criteria_test_all(Y=Y,X=X,Lambda=Lambda,dir_path=dir_path,maxrank=20)

criteria_test(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=20)
#criteria_fit(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=20)
rsbc_test(Y=Y,X=X,save=dir_path)
tp(save=dir_path)
```

```{r}
base_path <- here("out", "Soy")
res<-readRDS(file.path(base_path,"aic", "criteria.RDS"))
dir_path <- file.path(base_path, "aic")

res<-res[c(1,2,3,4,5,7,6),c(1,4,5,6,7,11,12,8,9)]
res<-t(res)


for (s in c(2,3,6,7)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(4,5,8,9)){
	res[s,]<-fd(res[s,],3)
}

for (s in c(3,5,7,9)) {
  res[s, ] <- paste0("(", res[s, ], ")")
}


xtable(res)

res<-readRDS(file.path(base_path,"aic", "criteria_alldata.RDS"))
#res<-res[,c(1,4,5,6,7,11,12,8,9)]
res<-res[c(1,2,3,4,5,7,6),]
res<-t(res)

for (s in c(2)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(3,4)){
	res[s,]<-fd(res[s,],3)
}


xtable(res)
tp(save=dir_path)
```

# methylation

But the rrr function (from rrpack package) or StARS dont work with this size of data because its more than memory 64GB.

```{r}
MethData<-readRDS(here("RDAdata","Methdata.RDS"))
base_path <- here("out", "Meth")
dir_path <- file.path(base_path, "aic")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 

gexp <- MethData$gexp
methy <- MethData$methy

Y <- gexp
X <- methy
```

Error: vector memory limit of 64.0 Gb reached, see mem.maxVSize()

```{r}
set.seed(123)
rn_list <- list()

for (k in 1:nrow(X)) {
  rn_list[[k]] <- k
}
saveRDS(rn_list,file.path(base_path, "rn_list.RDS"))
lm<-get_lambda_stars(dir_path, rn_list, Y=Y, X=X) 

```

```{r}
set.seed(123)

rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))
lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))

Lambda<-rrr_lambda(Y = Y, X = X)
criteria_test_all(Y=Y,X=X,Lambda=Lambda,dir_path=dir_path,maxrank=20)

criteria_test(Y=Y,X=X,num=100,Lambda=NULL,rn_list=NULL,lm=NULL,dir_path=dir_path,maxrank=15,oneout=T)

```
only rrdaworks..
```{R}
set.seed(123)
save <- file.path(base_path,"RS_mm")

Y<-gexp
X<-methy
#Lambda <- 10^seq(0, 6, length.out = 50)
rsbc(Y=Y,X=X,num=20,maxrank=15,save=save,sample=1,Lambda=NULL,oneout = T,nfold=5)

```


```{R}
tp(save=save)
```

# session info
check the info and environment
```{r}
devtools::session_info()
```
