---
title: "Application : Random Splitting on Application Data"
output: html_document
author: "Hayato Yoshioka (University of Tokyo, AgroParisTech)"
---

# Overview. H.Yoshioka et al. (rrda package)

Compare the rrda and stars, and other general criteria for parameter tuning and test to compute MSPE
For applications (Breast Cancer (ch13, ch all), Soybean)

Test with our lambda range selection rule.


# functions
```{r}
library(furrr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(RSpectra)
library(rrda)
library(here)
library(xtable)
library(pheatmap)
library(tictoc)
source("script_rrda/functions_rrda_yoshioka.R")
source("script_rrda/functions_stars_rrr_yoshioka.R")
```


# chrom 13 only
```{r,eval=T}
da<-readRDS(here("RDAdata","breast.RDS"))
base_path <- here("out", "BreastCancer")
dir_path <- file.path(base_path, "aic_ch13")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 

dna<-t(da$dna)
rna<-t(da$rna)
dch<-da$chrom
rch<-da$genechr
rch[is.na(rch)]<-0

Y<-dna[,dch==13]
X<-rna[,rch==13]
```

make rabdom sampling rule
make lambda accoring to rrda

```{R,eval=F}
set.seed(123)

rn_list <- list()

for (k in 1:100) {
  rn_list[[k]] <- sample(c(1:nrow(Y)), 10, replace = FALSE)
}
saveRDS(rn_list,file.path(base_path, "rn_list.RDS"))
lm<-get_lambda_rrda(dir_path, rn_list, Y=Y, X=X) 

```


criteria comparison (stars included)
```{r,eval=F}
set.seed(123)

lm<-readRDS(file.path(dir_path, "rrda_lambda.RDS"))
rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))

#Lambda<-rrr_lambda(Y = Y, X = X)
#criteria_test_all(Y=Y,X=X,Lambda=Lambda,dir_path=dir_path,maxrank=10)

criteria_test_rrdarange(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)
#criteria_fit(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=15)
rsbc_test_rrda(Y=Y,X=X,save=dir_path)
tp_rrda(save=dir_path)
```



```{r,eval=F}
rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))
lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))
criteria_fit_ann(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)
```

results
```{r}
base_path <- here("out", "BreastCancer")
dir_path <- file.path(base_path, "aic_ch13")
res<-readRDS(file.path(base_path,"aic_ch13", "criteria2.RDS"))



res<-res[c(1,2,3,4,5,7,6),c(1,4,5,6,7,11,12,8,9)]
res<-t(res)
res
for (s in c(2,3,6,7)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(4,5,8,9)){
	res[s,]<-fd(res[s,],3)
}

for (s in c(3,5,7,9)) {
  res[s, ] <- paste0("(", res[s, ], ")")
}

xtable(res)

res[,7]

```

#ch all

```{R}
da<-readRDS(here("RDAdata","breast.RDS"))
base_path <- here("out", "BreastCancer")
dir_path <- file.path(base_path, "aic_all")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 

dna<-t(da$dna)
rna<-t(da$rna)
dch<-da$chrom
rch<-da$genechr
rch[is.na(rch)]<-0

Y<-dna
X<-rna
```

make rabdom sampling rule
make lambda accoring to rrr (and stars)
```{R,eval=F}
set.seed(123)

rn_list <- list()

for (k in 1:100) {
  rn_list[[k]] <- sample(c(1:nrow(Y)), 10, replace = FALSE)
}
saveRDS(rn_list,file.path(base_path, "rn_list.RDS"))
lm<-get_lambda_rrda(dir_path, rn_list, Y=Y, X=X) 
```

all and rs
```{r,eval=F}
set.seed(123)
lm<-readRDS(file.path(dir_path, "rrda_lambda.RDS"))
rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))

criteria_test_rrdarange(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=63,criteria= c("rrda"))
rsbc_test_rrda(Y=Y,X=X,save=dir_path)
tp_rrda(save=dir_path)

```



```{r,eval=F}
rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))
lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))
criteria_fit_ann(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)
```


table
```{r}
base_path <- here("out", "BreastCancer")
dir_path <- file.path(base_path, "aic_all")
res<-readRDS(file.path(base_path,"aic_all", "criteria2.RDS"))
res<-res[c(1,2,3,4,5,7,6),c(1,4,5,6,7,11,12,8,9)]
res<-t(res)


for (s in c(2,3,6,7)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(4,5,8,9)){
	res[s,]<-fd(res[s,],3)
}

for (s in c(3,5,7,9)) {
  res[s, ] <- paste0("(", res[s, ], ")")
}

xtable(res)


```


# soybean

```{r}
base_path <- here("out", "Soy")
dir_path <- file.path(base_path, "aic")

if (!dir.exists(dir_path)) {
  dir.create(dir_path, recursive = TRUE)
  message("Directory created: ", dir_path)
} 

SoyData<-readRDS(here("RDAdata","Soydata.RDS"))
met <- SoyData$metabolome
micro <- SoyData$microbiome

Y <- met
X <- micro
```

```{R,eval=F}
set.seed(123)

rn_list <- list()

for (k in 1:100) {
  rn_list[[k]] <- sample(c(1:nrow(Y)), 20, replace = FALSE)
}
saveRDS(rn_list,file.path(base_path, "rn_list.RDS"))
lm<-get_lambda_rrda(dir_path, rn_list, Y=Y, X=X) 
```

all and rs
```{r,eval=F}
set.seed(123)
lm<-readRDS(file.path(dir_path, "rrda_lambda.RDS"))
rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))

criteria_test_rrdarange(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=20,criteria= c("rrda"))
rsbc_test_rrda(Y=Y,X=X,save=dir_path)
tp_rrda(save=dir_path)

```

```{r,eval=F}
rn_list <-readRDS(file.path(base_path, "rn_list.RDS"))
lm<-readRDS(file.path(dir_path, "aic_lambda.RDS"))
criteria_fit_ann(Y=Y,X=X,num=100,Lambda=NULL,rn_list=rn_list,lm=lm,dir_path=dir_path,maxrank=10)
```

```{r}
base_path <- here("out", "Soy")
res<-readRDS(file.path(base_path,"aic", "criteria2.RDS"))

res<-res[c(1,2,3,4,5,7,6),c(1,4,5,6,7,11,12,8,9)]
res<-t(res)


for (s in c(2,3,6,7)){
	res[s,]<-rd(res[s,],2)
}

for (s in c(4,5,8,9)){
	res[s,]<-fd(res[s,],3)
}

for (s in c(3,5,7,9)) {
  res[s, ] <- paste0("(", res[s, ], ")")
}
res[,1]

xtable(res)
```




# session info
check the info and environment
```{r}
devtools::session_info()
```
