
---
title: "Application : Breast Cancer (Model comparison of All to each chromosome and each to each chromosome)"
output: html_document
author: "Hayato Yoshioka (University of Tokyo, AgroParisTech)"
---

# Overview. H.Yoshioka et al. (rrda package)

Breast cancer data
Model comparison of All to each chromosome and each to each chromosome

# functions
```{r}
library(furrr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(RSpectra)
library(rrda)
library(PMA)
library(here)
library(xtable)
library(pheatmap)
library(tictoc)
source("script_rrda/functions_rrda_yoshioka.R")
source("script_rrda/functions_stars_rrr_yoshioka.R")
```
To install breast cancer data from PMA (Witten et al. 2024)

The data is also available on github https://github.com/Yoska393/rrda/tree/main/RDAdata)
```{}
library(PMA)
da<-download_breast_data()
```


# data
```{r,eval=T}

da<-readRDS(here("RDAdata","breast.RDS"))

dna<-t(da$dna)
rna<-t(da$rna)
dch<-da$chrom
rch<-da$genechr
table(is.na(rch))
table(is.na(dch))
rch[is.na(rch)]<-0

dim(dna)
dim(rna)
length(dch)
length(rch)

```

The model comparison
Whole genome to each chromosome model vs Each cheromosome to each chromosome.
Tested for 100 times by random splitting process (10 sampling for test)
Performed for 23 chromosomes

```{r}
set.seed(123)
chr_numbers <- 1:23

# Base path for saving results
base_path <- here("out", "BreastCancer")

for (chr in chr_numbers) {
  # Paths for the current chromosome
  path_allto_chr <- file.path(base_path, paste0("allto_chr", chr))
  path_chr <- file.path(base_path, paste0("chr", chr))
  
  if (!dir.exists(path_allto_chr)) {
    dir.create(path_allto_chr, recursive = TRUE)
  }
  if (!dir.exists(path_chr)) {
    dir.create(path_chr, recursive = TRUE)
  }
  
  # Execute rsbc function for each dynamic path
  rsbc(Y = dna[, dch == chr], X = rna, num = 100, maxrank = 15, save = path_allto_chr,sample=10)
  rsbc(Y = dna[, dch == chr], X = rna[, rch == chr], num = 100, maxrank = 15, save = path_chr,sample=10)

  # Compare the results from both paths
  compare(path_allto_chr, path_chr, num=100,chr = chr)
}
```


Results details
```{r,warning=FALSE,fig.width=6,fig.height=6}
set.seed(123)
chr_numbers <- 1:23
num<-100

base_path <- here("out", "BreastCancer")
chm<-matrix(NA,num,max(chr_numbers))
cham<-matrix(NA,num,max(chr_numbers))
chm_mspe<-matrix(NA,num,max(chr_numbers))
cham_mspe<-matrix(NA,num,max(chr_numbers))
for (chr in chr_numbers) {
  # Paths for the current chromosome
  path_allto_chr <- file.path(base_path, paste0("allto_chr", chr))
  path_chr <- file.path(base_path, paste0("chr", chr))
  
  if (!dir.exists(path_allto_chr)) {
    dir.create(path_allto_chr, recursive = TRUE)
  }
  if (!dir.exists(path_chr)) {
    dir.create(path_chr, recursive = TRUE)
  }
  tp(path_allto_chr)
  f<- compare(path_allto_chr, path_chr, num=num,chr = chr,model = 1)
  #print(f)
  chm[,chr]<- f$ch
  cham[,chr]<-f$ch_all
  
  chm_mspe[,chr]<- f$ch_mspe
  cham_mspe[,chr]<-f$ch_all_mspe
  
}
```

Boxplot of results. Only chromosome 7 was better with the whole genome data.
In general, the model is better when trained and tested within the chromosome.
```{r}
df_chm <- as.data.frame(chm)
df_cham <- as.data.frame(cham)
names(df_chm) <- paste0(1:23)
names(df_cham) <- paste0(1:23)
df_chm$group <- 'Chr to Chr'
df_cham$group <- 'Whole to Chr'
combined_df <- rbind(df_chm, df_cham)
melted_df <- melt(combined_df, id.vars='group')
ggplot(melted_df, aes(x=variable, y=value, fill=group)) +
  geom_boxplot(outlier.shape = NA) +
  theme_minimal() +
  labs(title="COR (Chr all vs Chr each)", x="Chromosome", y="COR") +
  scale_fill_manual(values=c("blue", "orange"))

```
MSPE
```{r}
df_chm <- as.data.frame(chm_mspe)
df_cham <- as.data.frame(cham_mspe)
names(df_chm) <- paste0(1:23)
names(df_cham) <- paste0(1:23)
df_chm$group <- 'Chr to Chr'
df_cham$group <- 'Whole to Chr'
combined_df <- rbind(df_chm, df_cham)
melted_df <- melt(combined_df, id.vars='group')
ggplot(melted_df, aes(x=variable, y=value, fill=group)) +
  geom_boxplot(outlier.shape = NA) +
  theme_minimal() +
	ylim(c(0, 15)) +
  labs(title="MSPE (Chr all vs Chr each)", x="Chromosome", y="MSPE") +
  scale_fill_manual(values=c("blue", "orange"))

```


# session info
check the info and environment
```{r}
devtools::session_info()
```
